O give thanks unto the Lord, for He is good; for His mercy endureth for ever.

Let the redeemed of the Lord say so, whom He hath redeemed from the hand of the enemy, and gathered them out of the lands; from the east, and from the west, and from the north, and from the sea.

They wandered in the wilderness in a way, in a waterless place; they found not the way to a city of habitation.

Hungry and thirsty, their soul fainted in them.

Then they cried unto the Lord in their trouble, and He delivered them out of their distresses.

And He led them forth into the right way, that they might go to a city of habitation.

Let them praise the Lord for His mercies, and for His wonderful works to the children of men.

For He hath satisfied the empty soul, and filled the hungry soul with goodness.

Such as sit in darkness and in the shadow of death, bound in poverty and iron,

Because they rebelled against the words of God, and provoked the counsel of the Most High.

Their heart also was brought down with labours; they grew feeble and there was none to help.

Then they cried unto the Lord in their trouble, and He saved them out of their distresses.

And He brought them out of darkness, and the shadow of death; and brake their bonds asunder.

Let them praise the Lord for His mercies, and for His wonderful works to the children of men.

For He hath broken the gates of brass, and shattered the bars of iron.

He helped them out of the way of their transgressions, for they were brought low because of their iniquities.

Their soul abhorred all manner of meat, and they drew near unto the gates of death.

And they cried unto the Lord in their trouble, and He saved them out of their distresses.

He sent his Word, and healed them, and delivered them from their corruption.

Let them praise the Lord for His mercies, and for His wonderful works to the children of men.

And let them sacrifice to Him a sacrifice of praise, and declare His works with gladness.

They that go down to the sea in ships, that do their business in great waters;

These men have seen the works of the Lord, and His wonders in the deep.

He spake the word, and a storm of wind arose; and the waves thereof were lifted up.

They mount up to the heavens, and they go down into the depths; their soul melted away with evils.

They were troubled, and they staggered as a drunken man; and all their wisdom was swallowed up.

Then they cried unto the Lord in their trouble, and He brought them out of their distresses.

And He commanded the storm, and it was calmed into a breeze; and the waves thereof fell silent.

Then were they glad, because they were stilled; and He guided them unto the haven of His will.

Let them praise the Lord for His mercies, and for His wonderful works to the children of men.

Let them exalt Him in the congregation of the people, and praise Him in the seat of the elders.

He hath turned rivers into a wilderness, and the springs of waters into dry ground;

A fruitful land into saltness, for the wickedness of them that dwell therein.

He turned a wilderness into pools of waters, and a parched land into streams of waters.

And there He made the hungry to dwell, and they prepared cities for habitation,

And sowed the fields, and planted vineyards, which yielded fruits of increase.

He blessed them also, so that they were multiplied greatly; and He suffered not their cattle to decrease.

And again, they were diminished and brought low through affliction, evils, and sorrow.

Contempt was poured upon their princes; and He caused them to wander in a wilderness, where there is no way.

And He helped the poor out of his poverty, and made his families like a flock.

The upright shall see it, and rejoice, and all iniquity shall stop her mouth.

Who is wise, and will observe these things, and will understand the mercy of the Lord?
