When Israel went out of Egypt, the house of Jacob from among a barbarous people,

Judah was his sanctuary, and Israel his dominion.

The sea saw it, and fled; Jordan was driven back.

The mountains skipped like rams, and the hills like lambs of the flock.

What ailed thee, O sea, that thou fleddest? and thou, Jordan, that thou wast driven back?

Ye mountains, that ye skipped like rams, and ye hills, like lambs of the flock?

The earth trembled at the presence of the Lord, at the presence of the God of Jacob.

Who turneth the rock into pools of water, and the sharp rock into fountains of water.

Not unto us, Lord, not to us, but unto Thy Name give glory, for Thy mercy and truth’s sake.

Lest the heathen should say, Where is their God?

But our God is in the heavens and on earth; He hath done whatsoever He pleased.

The idols of the heathen are of silver and gold, the work of men’s hands.

They have a mouth, but they speak not; they have eyes, but they see not.

They have ears, but they hear not; noses have they, but they smell not.

They have hands, but they handle not; feet have they, but they walk not; neither speak they through their throat.

Let them that make them become like unto them, yea, all who put their trust in them.

The house of Israel hath hoped in the Lord; He is their help, and their defender.

The house of Aaron hath hoped in the Lord; He is their help, and their defender.

They that fear the Lord have hoped in the Lord; He is their help, and their defender.

The Lord hath been mindful of us, and hath blessed us; He hath blessed the house of Israel, He hath blessed the house of Aaron.

He hath blessed them that fear the Lord, both small and great.

The Lord increase you, you and your children.

Ye are blessed of the Lord, which made heaven and earth.

The heaven of heavens is the Lord's, but the earth hath He given to the children of men.

The dead shall not praise Thee, O Lord, neither any that go down into hades.

But we who live will bless the Lord, from henceforth and for evermore.
