Lord, Thou hast been our refuge in generation and generation.

Before the mountains were brought forth, and the earth and the world were formed, from everlasting to everlasting Thou art.

Turn not man away to lowliness; Thou hast said, Return, ye children of men.

For a thousand years in Thy sight, O Lord, are but as yesterday which is past, and as a watch in the night.

Things of no account shall their years be; in the morning as the grass shall man pass away.

In the morning he shall flourish, and pass away, in the evening he shall fall, and become withered and dry.

For we have fainted in Thine anger, and have been troubled in Thy wrath.

Thou hast set our iniquities before Thee, our life in the light of Thy countenance.

For all our days are spent, and in Thy wrath have we fainted away; our years like a spider have spun out their tale.

The days of our years are threescore years and ten, and if webe in strength, then fourscore years; and more than these is labour and travail, for weakness is come upon us, and we shall be
chastened.

Who knoweth the power of Thine anger? and for fear of Thee who can recount Thy wrath?

So make Thy right hand known to me, and to them that are learned in heart in wisdom.

Return, O Lord, how long? and be Thou entreated for Thy servants.

We have been satisfied early with Thy mercy, O Lord, and we have rejoiced, and been glad.

Let us be glad all our days for the days wherein Thou hast humbled us, for the years wherein we have seen evils.

And look upon Thy servants, and upon Thy works, and guide Thou their sons.

And let the brightness of the Lord our God be upon us; prosper Thou the work of our hands upon us, yea, the work of our hands prosper Thou upon us.
