O give thanks unto the Lord, for He is good; for His mercy endureth for ever.

O give thanks unto the God of gods; for His mercy endureth for ever.

O give thanks unto the Lord of lords; for His mercy endureth for ever.

To Him who alone hath done great wonders; for His mercy endureth for ever.

To Him that by wisdom made the heavens; for His mercy endureth for ever.

To Him that established the earth upon the waters; for His mercy endureth for ever.

To Him that alone made great lights; for His mercy endureth for ever.

The sun to rule the day; for His mercy endureth for ever.

The moon and the stars to rule the night; for His mercy endureth for ever.

To Him that smote Egypt in their firstborn; for His mercy endureth for ever.

And brought out Israel from among them; for His mercy endureth for ever.

With a strong hand, and with an upraised arm; for His mercy endureth for ever.

To Him which divided the Red Sea into parts; for His mercy endureth for ever.

And led Israel through the midst of it; for His mercy endureth for ever.

And overthrew Pharao and his host in the Red Sea; for His mercy endureth for ever.

To Him which led His people through the wilderness; for His mercy endureth for ever.

To Him which smote great kings; for His mercy endureth for ever.

And slew mighty kings; for His mercy endureth for ever.

Sehon, king of the Amorites; for His mercy endureth for ever.

And Og, the king of Basan; for His mercy endureth for ever.

And gave their land for an heritage; for His mercy endureth for ever.

Even an heritage unto Israel His servant; for His mercy endureth for ever.

For the Lord remembered us in our low estate; for His mercy endureth for ever.

And hath redeemed us from our enemies; for His mercy endureth for ever.

Who giveth food to all flesh; for His mercy endureth for ever.

O give thanks unto the God of heaven; for His mercy endureth for ever.
