Deliver me from mine enemies, O God, and redeem me from them that rise up against me.

Deliver me from the workers of iniquity, and save me from the bloodthirsty men.

For lo, they have hunted after my soul, the mighty have set upon me; not for mine iniquity, nor for my sin, O Lord.

Without iniquity I ran, and directed my steps; arise Thou to meet me, and behold.

Thou, therefore, O Lord God of hosts, the God of Israel, draw near to visit all the heathen; be not merciful to any that work iniquity.

They shall return at evening, and hunger like dogs, and go round about the city.

Behold, they shall utter a sound with their mouth, and a sword is in their lips: For who, say they, hath heard?

But Thou, O Lord, shalt laugh at them; Thou shalt bring all the heathen to nought.

O my strength, I will keep watch for Thee, for Thou, O God, art my help.

As for my God, His mercy shall prevent me; God shall reveal it unto me among mine enemies.

Slay them not, lest they forget Thy law: scatter them by Thy power, and bring them down, O Lord my defender.

For the sin of their mouth, and the words of their lips, let them even be taken in their pride.

And for their cursing and lying shall their utter destruction be made known, in the wrath of utter destruction.

And they shall be no more, and they shall know that God is Lord of Jacob, and of the ends of the earth.

They shall return at evening, and hunger like dogs, and go round about the city.

They shall be scattered abroad to eat; they shall murmur if they be not satisfied.

But I will sing of Thy strength; yea, I will rejoice in Thy mercy in the morning. For Thou art become my help and my refuge in the day of my trouble.

Thou art my help, unto Thee will I sing, for Thou, O God, art my help; my God, Thou art my mercy.
