Hear this, all ye heathen; give ear, all ye inhabitants of the world.

All ye that were born of earth, and ye sons of men; rich and poor together.

My mouth shall speak of wisdom, and the meditation of my heart shall be of understanding.

I will incline mine ear to a parable; I will open my dark saying upon the psaltery.

Wherefore should I fear in the day of evil? The iniquity at my heel shall compass me about.

There be some that trust in their strength, and boast themselves in the multitude of their riches.

A brother cannot redeem; shall a man redeem?

He cannot give to God a ransom for himself, nor the price of the redemption of his soul, even though he hath laboured for ever, and shall live to the end.

For he shall not see corruption, when he seeth wise men die. The unwise and the fool shall perish together, and leave their wealth to others.

And their graves shall be their houses for ever, their dwelling places unto generation and generation; though they have called their lands after their own names.

Nevertheless, man being in honour understood not; he is like the cattle that are without understanding, and is become like unto them.

This their way is a stumbling block for them, yet afterwards they shall please with their mouth.

Like sheep they are laid in hades; death shall be their shepherd.

And the upright shall have dominion over them in the morning, and from their glory their help shall rot in hades.

But God will redeem my soul out of the hand of hades, when He receiveth me.

Be not thou afraid when one is made rich, or when the glory of his house is increased.

For when he dieth, he shall carry nothing away; his glory shall not descend after him.

For his soul shall be blessed in his life; he will acknowledge Thee when Thou doest well to him.

He shall go to the generation of his fathers; he shall never see the light.

And man that is in honour, understood not; he is like the cattle that are without understanding, and is become like unto them.
