My heart hath poured forth a good word; I speak of my works to the King. My tongue is the pen of a ready writer.

Thou art fairer than the children of men; grace is poured upon Thy lips; therefore God hath blessed Thee for ever.

Gird Thy sword upon Thy thigh, O mighty one, in Thy comeliness and in Thy beauty.

And bend thy bow, and prosper, and reign, because of truth and meekness and righteousness; and Thy right hand shall guide Thee wondrously.

Thine arrows are sharp, O mighty one, in the heart of the King’s enemies; the peoples shall fall under Thee.

Thy throne, O God, is for ever and ever; the sceptre of Thy kingdom is a sceptre of uprightness.

Thou hast loved righteousness, and hated wickedness; therefore God, thy God hath anointed thee with the oil of gladness above thy fellows.

Myrrh and stacte and cassia are from thy garments, out of the ivory palaces, whereby they have made thee glad, the daughters of kings in thine honour.

Upon Thy right hand did stand the queen in raiment of woven gold, arrayed in divers colours.

Hearken, O daughter, and consider, and incline thine ear; forget also thine own people, and thy father's house.

And the King shall greatly desire thy beauty, for He is thy Lord, and thou shalt worship Him.

And the daughters of Tyre shall worship him with gifts; even the rich among the people shall entreat thy countenance.

All the glory of the King’s daughter is within; in fringed gold is she arrayed, wrought about with divers colours.

The virgins that follow her shall be brought unto the King; her fellows shall be brought unto Thee.

With gladness and rejoicing shall they be brought, they shall be brought into the temple of the King.

Instead of thy fathers sons are born to thee; thou shalt make them princes over all the earth.

I will remember thy name in every generation and generation. Therefore shall the peoples praise thee for ever, and unto the ages of ages.
