Praise ye the name of the Lord; O ye servants, praise the Lord,

Ye that stand in the house of the Lord, in the courts of the house of our God.

Praise the Lord, for the Lord is good; sing praises unto His name, for it is good.

For the Lord hath chosen Jacob unto Himself, and Israel for His own possession.

For I know that the Lord is great, and that our Lord is above all gods.

Whatsoever the Lord willed, that did He in heaven, and in earth, in the seas and all deep places.

He bringeth up clouds from the ends of the earth; He made lightnings for the rain; He bringeth the winds out of His treasuries.

Who smote the firstborn of Egypt, from man to beast.

He sent tokens and wonders into the midst of thee, O Egypt; unto Pharao, and unto all his servants.

Who smote many nations, and slew mighty kings:

Sehon, king of the Amorites, and Og, the king of Basan; and all the kingdoms of Chanaan.

And gave their lands for an heritage, an heritage unto Israel His people.

Thy name, O Lord, endureth for ever; and Thy memorial unto generation and generation.

For the Lord will judge His people, and comfort Himself because of His servants.

The idols of the heathen are silver and gold, the work of men's hands.

They have a mouth, but they speak not; eyes have they, but they see not.

They have ears, but they hear not; neither is there any breath in their mouths.

Let those who make them be like unto them, and every one that trusteth in them.

Bless the Lord, O house of Israel: bless the Lord, O house of Aaron: bless the Lord, O house of Levi.

Ye that fear the Lord, bless the Lord. Blessed be the Lord out of Sion, which dwelleth at Jerusalem.
