O God, the heathen are come into Thine inheritance, Thy holy temple have they defiled; they have made Jerusalem as an orchard watcher’s hut.

The dead bodies of Thy servants have they given to be meat unto the fowls of the heaven, the flesh of Thy saints unto the beasts of the earth.

Their blood have they shed like water round about Jerusalem, and there was none to bury them.

We are become a reproach to our neighbours, a scorn and derision to them that are round about us.

How long, O Lord? wilt Thou be angry for ever? Shall Thy jealousy be kindled like fire?

Pour out Thy wrath upon the heathen that have not known Thee, and upon the kingdoms that have not called upon Thy name.

For they have devoured Jacob, and laid waste his dwelling place.

O remember not our former iniquities; let Thy tender mercies speedily prevent us, Lord, for we are become exceeding poor.

Help us, O God our Saviour, for the glory of Thy name; deliver us, O Lord, and be gracious unto our sins for Thy name's sake.

Lest the heathen say, Where is their God? Yea, make known among the heathen in our sight the vengeance for the blood of Thy servants which hath been shed.

Let the groaning of the prisoners come before Thee; according to the greatness of Thine arm show Thy care for the sons of the slain.

And render unto our neighbours sevenfold into their bosom their reproach wherewith they have reproached Thee, O Lord.

For we are Thy people, and the sheep of Thy pasture. We will give Thee thanks, O God, for ever; we will show forth Thy praise from generation to generation.
