O God, why hast Thou cast us off for ever? Why hath Thine anger raged against the sheep of Thy pasture?

Remember Thy congregation, which Thou hast purchased of old.

Thou hast redeemed the rod of Thine inheritance, this Mount Sion wherein Thou hast dwelt.

Lift up Thy hands against their perpetual pride, even all that the enemy hath done wickedly in Thy sanctuary.

And they that hate Thee have made their boast in the midst of Thy feast.

They set up their ensigns for signs, though they knew it not, in the going out on high.

As in a forest of trees, they have cut down at once the doors thereof with axes; they have broken it down with axe and hammer.

With fire have they burned down Thy sanctuary; they have defiled the dwelling place of Thy name to the ground.

They said in their heart, the whole kindred of them together, Come, let us abolish all the feasts of God from the earth.

We have not seen our signs, there is no more any prophet, and he will know us no more.

O God, how long shall the enemy reproach? Shall the enemy provoke Thy name for ever?

Why withdrawest Thou Thy hand, even Thy right hand, out of the midst of Thy bosom for ever?

But God is our king of old; He hath wrought salvation in the midst of the earth.

Thou didst establish the sea by Thy strength; Thou brakest the heads of the dragons in the water.

Thou didst crush the head of the dragon; Thou gavest him to be meat to the people of the Ethiopians.

Thou didst cleave the fountains and the floods, Thou driedst up the rivers of Etham.

The day is Thine, the night also is Thine; Thou hast prepared the light and the sun.

Thou hast set all the borders of the earth; Thou hast made the summer and spring.

Remember this Thy creation. The enemy hath reproached the Lord, and a foolish people hath provoked Thy name.

O deliver not over unto the wild beasts the soul that doth confess Thee; forget not the souls of Thy poor for ever.

Have respect unto Thy covenant, for the dark places of the earth are filled with the habitations of iniquity.

Let not the humble and ashamed be turned away; the poor and the needy shall praise Thy name.

Arise, O God, judge Thine own cause; remember the reproach that is made against Thee daily by the foolish man.

Forget not the voice of Thy suppliants; the pride of those that hate Thee riseth up continually.
