Give Thy judgment, O God, to the King, and Thy righteousness unto the King's Son.

That He may judge Thy people with righteousness, and Thy poor with judgment.

Let the mountains receive peace for the people, and the hills righteousness.

He shall judge the poor of the people, and shall save the children of the needy, and shall humble the false accuser.

And He shall continue as long as the sun, and before the moon, from generation to generation.

He shall come down like rain upon a fleece, and as raindrops that fall upon the earth.

In His days shall righteousness spring up, and abundance of peace, until the moon be taken away.

He shall have dominion also from sea to sea, and from the rivers unto the ends of the earth.

The Ethiopians shall fall down before Him, and his enemies shall lick the dust.

The kings of Tharsis and of the isles shall bring presents; the kings of the Arabians and Saba shall offer gifts.

Yea, all the kings of the earth shall worship Him; all nations shall serve Him.

For He hath delivered the poor from the oppressor, the needy also, which had no helper.

He shall spare the poor and needy, and shall save the souls of the needy.

He shall redeem their souls from usury and injustice, and precious shall His Name be in their sight.

And He shall live, and to Him shall be given of the gold of Arabia; and they shall pray for Him continually, all the day shall they bless Him.

He shall be a firmament in the earth upon the tops of the mountains; the fruit thereof shall be exalted above Lebanon, and they of the city shall flourish like grass of the earth.

His Name shall be blessed for ever; His Name continueth before the sun. And in Him shall all the tribes of the earth be blessed; all nations shall call Him blessed.

Blessed be the Lord God of Israel, who only doeth wondrous things.

And blessed be the Name of His glory for ever, yea, for ever and ever.

And all the earth shall be filled with His glory. So be it. So be it.
