Make a joyful noise unto the Lord, all the earth.

Sing praises unto His Name, give glory in His praise.

Say unto God, How terrible are Thy works! Through the greatness of Thy power shall Thine enemies be found false unto Thee.

Let all the earth worship Thee, and sing unto Thee; let them sing to Thy Name, O Thou Most High.

Come and see the works of God, terrible in His counsels over the children of men.

He turneth the sea into dry land; they shall go through the flood on foot; there shall we rejoice in Him,

Who ruleth by His power for ever. His eyes behold the nations; let not them that embitter Him be exalted in themselves.

O bless our God, ye people, and make the voice of His praise to be heard,

Which holdeth my soul in life, and suffereth not my feet to be moved.

For Thou, O God, hast proved us, and hast tried us by fire, as silver is tried.

Thou broughtest us into the snare, Thou laidst afflictions upon our back.

Thou didst set men over our heads; we went through fire and through water, but Thou broughtest us out into refreshment.

I will go into Thy house with a whole burnt offering; I will pay Thee my vows, which my lips have uttered, and my mouth hath spoken, when I was in trouble.

I will offer unto Thee burnt sacrifices, full of marrow, with the incense of rams; I will offer Thee bullocks with goats.

Come and hear, all ye that fear God, and I will declare what He hath done for my soul.

I cried unto Him with my mouth, and extolled Him with my tongue.

If I have regarded iniquity in my heart, let not the Lord hear me.

But verily God hath heard me; He hath attended to the voice of my prayer.

Blessed be God, which hath not turned away my prayer, nor His mercy from me.
