Fret not thyself because of evil doers, neither be thou envious against the workers of iniquity.

For they shall soon be withered like the grass, and shall quickly fall away, like the green herb.

Hope in the Lord, and do good; and dwell in the land, and thou shalt be fed with its riches.

Delight thyself in the Lord, and He shall give thee the desires of thine heart.

Disclose thy way unto the Lord; hope also in him; and He shall bring it to pass.

And He shall bring forth thy righteousness as the light, and thy judgment as the noonday.

Submit thyself unto the Lord, and entreat thou Him; fret not thyself because of him who prospereth in his way, because of the man who bringeth wicked devices to pass.

Cease from anger, and forsake wrath; fret not thyself in any wise to do evil.

For evil doers shall be cut off; but those that wait upon the Lord, they shall inherit the earth.

For yet a little while, and the wicked shall not be; yea, thou shalt diligently consider his place, and shalt not find it.

But the meek shall inherit the earth, and shall delight themselves in the abundance of peace.

The sinner shall watch for the just, and gnash upon him with his teeth.

But the Lord shall laugh at him, for He seeth that his day is coming.

The wicked have drawn out the sword, they have bent their bow; to cast down the poor and needy, to slay such as be of an upright heart.

Let their sword enter into their own heart, and let their bows be broken.

Better is a little that the righteous man hath than the many riches of the wicked.

For the arms of the wicked shall be broken, but the Lord upholdeth the righteous.

The Lord knoweth the ways of the blameless, and their inheritance shall be for ever.

They shall not be ashamed in the evil time, and in the days of famine they shall be satisfied.

For the wicked shall perish, and the enemies of the Lord, in the moment when they are glorified and exalted, shall vanish like smoke.

The wicked borroweth, and payeth not again; but the righteous showeth mercy, and giveth.

For they that bless Him shall inherit the earth; but they that curse Him shall perish.

The steps of a man are ordered by the Lord, and He shall delight in his way.

Though he fall, he shall not be utterly cast down, for the Lord upholdeth his hand.

I have been young, and now am old; yet I have not seen the righteous forsaken, nor his seed begging bread.

The righteous is merciful, and lendeth all the day long, and his seed shall be blessed.

Depart from evil, and do good; and dwell for evermore.

For the Lord loveth judgment, and forsaketh not His saints; they shall be preserved for ever. But the wicked shall be banished, and the seed of the ungodly shall be cut off.

The righteous shall inherit the land, and dwell therein for ever.

The mouth of the righteous shall speak of wisdom, and his tongue shall talk of judgment.

The law of his God is in his heart, and his steps shall not be tripped.

The wicked watcheth the righteous, and seeketh to slay him.

But the Lord will not leave him in his hand, nor condemn him when He judgeth him.

Wait on the Lord, and keep His way, and He shall exalt thee to inherit the land; when the wicked are cut off, thou shalt see it.

I have seen the ungodly highly exalted, and lifting himself up like the cedars of Lebanon.

Yet I passed by, and lo, he was not; yea, I sought him, but his place could not be found.

Keep innocence, and behold uprightness, for there is a remnant for the man of peace.

But the transgressors shall be destroyed together; the remnant of the ungodly shall be cut off.

But the salvation of the righteous is of the Lord, and He iss their defence in the time of trouble.

And the Lord shall help them, and deliver them; and He shall deliver them from the ungodly, and save them, because they have hoped in Him.
