Look Thou upon me, and be merciful unto me, according to the judgment of those that love Thy Name.

Order my steps according to Thy word, and let not any iniquity have dominion over me.

Deliver me from the false accusation of men, and I will keep Thy commandments.

Make Thy face to shine upon Thy servant, and teach me Thy statutes.

Mine eyes have sent forth streams of water, because I kept not Thy law.

Righteous art Thou, O Lord, and upright are Thy judgments.

Thy testimonies that Thou hast commanded are very righteousness and truth.

My zeal for Thee hath made me to pine away, because mine enemies have forgotten Thy words.

Thy word hath been tried in the fire to the uttermost, and Thy servant hath loved it.

I am young and despised, yet have I not forgotten Thy statutes.

Thy righteousness is an everlasting righteousness, and Thy law is truth.

Troubles and anguish have found me, yet Thy commandments are my meditation.

Thy testimonies are righteousness for ever; give me understanding, and I shall live.

I cried with my whole heart; hear me, O Lord, and I shall seek Thy statutes.

I cried unto Thee; save me, and I shall keep Thy testimonies.

I rose up before the dawn, and cried; I hoped in Thy words.

Mine eyes awoke before the morning, that I might meditate in Thy words.

Hear my voice according unto Thy mercy, O Lord; quicken me according to Thy judgment.

They draw nigh that persecute me unlawfully; they are far from Thy law.

Thou art near, O Lord, and all Thy ways are truth.

Concerning Thy testimonies, I have known of old that Thou hast founded them for ever.

Behold my humiliation, and deliver me, for I have not forgotten Thy law.

Judge Thou my cause, and deliver me; quicken me according to Thy word.

Salvation is far from the wicked, for they have not sought Thy statutes.

Many are Thy tender mercies, O Lord; quicken me according to Thy judgment.

Many are they that persecute me and afflict me, yet have I not turned aside from Thy testimonies.

I beheld the foolish and was grieved, because they kept not Thy words.

See how I have loved Thy commandments; O Lord, quicken me in Thy mercy.

The beginning of Thy words is truth, and all the judgments of Thy righteousness endure for ever.

Princes have persecuted me without a cause, and my heart hath been afraid because of Thy words.

I will rejoice at Thy words, as one that findeth great spoil.

I have hated and abhorred injustice, but Thy law have I loved.

Seven times a day have I praised Thee because of the judgments of Thy righteousness.

Great peace have they that love Thy law, and for them there is no stumbling block.

Lord, I have looked for Thy salvation, and loved Thy commandments.

My soul hath kept Thy testimonies, and loved them exceedingly.

I have kept Thy commandments and Thy testimonies, for all my ways are before Thee, O Lord.

Let my prayer draw near to Thee, O Lord; give me understanding according to Thy word.

Let my supplication come before Thee, O Lord; deliver me according to Thy word.

My lips shall pour forth Thy praise, when Thou hast taught me Thy statutes.

My tongue shall speak of Thy words, for all Thy commandments are righteousness.

Let Thine hand be near to save me, for I have chosen Thy commandments.

I have longed for Thy salvation, O Lord; and Thy law is my study.

My soul shall live, and it shall praise Thee, and Thy judgments shall help me.

I have gone astray like a lost sheep; seek Thy servant, for I have not forgotten Thy commandments.
