Judge them, O Lord, that do me injustice; war against them that war against me.

Take hold of weapon and shield, and arise to my help.

Draw out the sword, and stop the way against them that persecute me; say unto my soul, I am Thy salvation.

Let them be confounded and put to shame that seek after my soul; let them be turned back and brought to confusion that devise my hurt.

Let them be as chaff before the face of the wind, and let the angel of the Lord afflict them.

Let their way be dark and a cause of slipping, and let the angel of the Lord pursue them.

For without cause have they hid for me destruction in their snare; without cause have they reproached my soul.

Let a snare come upon him unawares, and let the trap that he hath hid catch himself; and into that very snare let him fall.

But my soul shall be joyful in the Lord; it shall delight in His salvation.

All my bones shall say, Lord, Lord, who is like unto Thee, who deliverest the poor from the hand of them that are stronger than he, yea, the poor and the needy from them that spoil him?

False witnesses did rise up against me; asking me things that I knew not.

They rewarded me evil for good, and bereavement to my soul.

But as for me, when they troubled me, I put on sackcloth, and humbled my soul with fasting; and my prayer shall return into mine own bosom.

I sought to please, as if it had been my neighbour or brother; I bowed down heavily, as one mourning and sad of face.

But they rejoiced against me, and gathered themselves together; plagues were gathered together upon me, and I knew it not.

They were scattered, yet they repented not; they tempted me, they sneered at me with scorn, they gnashed upon me with their teeth.

Lord, when wilt Thou look upon me? Rescue my soul from their malice, mine only one from the lions.

I will give Thee thanks in the great congregation; I will praise Thee among a mighty people.

Let not them that are mine enemies wrongfully rejoice over me, they that hate me without a cause, and wink with the eye.

For they spake unto me peaceably indeed, but in their anger they devised deceits.

Yea, they opened their mouth wide against me; they said, it is well, it is well, our eyes have seen it.

This Thou hast seen, O Lord, keep not silence; O Lord, be not far from me.

Rise up, Lord, and attend to my judgment, even unto my cause, my God and my Lord.

Judge me, O Lord, according to Thy righteousness; let them not rejoice over me, O Lord my God.

Let them not say in their hearts, it is well, it is well, to our soul! Neither let them say, we have swallowed him up.

Let them be ashamed and brought to confusion together that rejoice at my woes. Let them be clothed with shame and confusion that magnify their words against me.

Let them rejoice and be glad, that favour the righteousness of my cause; and let them that desire the peace of Thy servant say continually, let the Lord be magnified.

And my tongue shall speak of Thy righteousness, and of Thy praise all the day long.
