Unto Thee, O Lord, have I lifted up my soul.

O my God, I have trusted in Thee, let me never be ashamed; neither let mine enemies laugh me to scorn.

Yea, let none that wait on Thee be ashamed; let them be ashamed which transgress without cause.

Show me Thy ways, O Lord, and teach me Thy paths.

Lead me in Thy truth, and teach me, for Thou art God my Saviour; for on Thee have I waited all the day.

Remember, O Lord, Thy tender mercies, and Thy lovingkindnesses; for they have been ever of old.

Remember not the sins of my youth, and my sins of ignorance; according to Thy mercy remember Thou me, for Thy goodness’ sake, O Lord.

Good and upright is the Lord; therefore will He give a law to
sinners in the way.

The meek will He guide in judgment, and the meek will He teach his ways.

All the paths of the Lord are mercy and truth, unto such as seek His covenant and His testimonies.

For Thy Name's sake, O Lord, pardon mine iniquity, for it is great.

What man is he that feareth the Lord? Him shall He give a law in the way that He hath chosen.

His soul shall dwell among good things, and his seed shall inherit the earth.

The Lord is the strength of them that fear Him, and His covenant shall be revealed to them.

Mine eyes are ever toward the Lord, for He shall pluck my feet out of the net.

Look Thou upon me, and have mercy upon me; for I am an only one and poor.

The troubles of my heart are enlarged; O bring Thou me out of my necessities.

Look upon my lowliness and my toil, and forgive all my sins.

Consider mine enemies, for they are multiplied, and they have hated me with unjust hatred.

O keep my soul, and deliver me; let me not be ashamed, for I have put my trust in Thee.

The innocent and the upright have cleaved to me, for I have waited on Thee, O Lord.

Redeem Israel, O God, out of all his troubles.
