In Thee, O Lord, have I put my hope, let me never be ashamed; deliver me in Thy righteousness, and rescue me.

Bow down Thine ear to me; deliver me speedily.

Be Thou unto me a defending God, and a house of refuge to save me.

For Thou art my strength and my refuge; therefore for Thy Name's sake shalt Thou guide and nourish me.

Thou shalt bring me out of this snare that they have laid privily for me; for Thou art my defender, O Lord.

Into Thy hands I will commit my spirit; Thou hast redeemed me, O Lord God of truth.

Thou hast hated them that hold to empty vanities, but I have hoped in the Lord.

I will be glad and rejoice in Thy mercy, for Thou hast considered my lowliness, Thou hast saved my soul out of adversities,

And hast not shut me up into the hand of the enemy; Thou hast set my feet in a large room.

Have mercy upon me, Lord, for I am in trouble; mine eye is troubled with anger, yea, my soul and my belly.

For my life is spent with grief, and my years with groaning; my strength hath been weakened through poverty, and my bones are
troubled.

I became a reproach among all mine enemies, but especially among my neighbours, and a fear to mine acquaintance. They that did see me without fled from me.

I am forgotten as a dead man out of mind; I am become like a broken vessel.

For I have heard the slander of many that dwell on every side; when they took counsel together against me, they devised to take away my life.

But I hoped in Thee, O Lord; I said, Thou art my God, my lots are in Thy hands.

Deliver me from the hand of mine enemies, and from them that persecute me.

Make Thy face to shine upon Thy servant; save me for Thy mercy’s sake.

Let me not be ashamed, O Lord, for I have called upon Thee; let the wicked be ashamed, and brought down into hell.

Let the lying lips be put to silence, which speak iniquity proudly and contemptuously against the righteous.

Oh how great is the multitude of Thy goodness, O Lord, which Thou hast laid up for them that fear Thee; which Thou hast wrought for them that trust in Thee before the sons of men!

Thou shalt hide them in the secret of Thy presence from the disturbance of men; Thou shalt keep them secretly in Thy pavilion from the strife of tongues.

Blessed be the Lord, for He hath marvellously showed His mercy in a fortified city.

But I said in my alarm, I am cut off from before Thine eyes. Nevertheless Thou heardest the voice of my supplication when I cried unto Thee.

O love the Lord, all ye His saints, for the Lord requireth truth, and rewardeth the proud doers.

Be of good courage, and let your heart be strengthened, all ye that hope in the Lord.
