O God my God, hear me; why hast Thou forsaken me? Far from my salvation are the words of my transgressions.

O my God, I will cry in the daytime, but Thou hearest not; and in the night season, and it shall not be folly unto me.

But Thou dwellest in the holy place, O Thou praise of Israel. In Thee our fathers hoped; they hoped, and Thou didst deliver them.

They cried unto Thee, and were delivered; they hoped in Thee, and were not ashamed.

But I am a worm, and no man; a reproach of men, and the outcast of the people.

All they that saw me laughed me to scorn; they spake with their lips, they shook their heads, saying:

He hoped in the Lord, let Him deliver him; let Him save him, seeing He delighteth in him.

For Thou are He that took me out of the womb; my hope, when I hanged yet upon my mother's breasts. I was cast upon Thee from the womb. From the womb of my mother, Thou art my God. Be not far from me.

For trouble is near, for there is none to help.

Many bullocks have compassed me; fat bulls have beset me round.

They have opened their mouths against me, as a ravening and roaring lion.

I am poured out like water, and all my bones are scattered; my heart is become like wax melting in the midst of my bowels.

My strength is dried up like a potsherd, and my tongue hath cleaved to my throat, and Thou hast brought me down into the dust of death.

For many dogs have compassed me, and the assembly of the wicked have enclosed me.

They have pierced my hands and my feet, they have numbered all my bones, and they have looked and stared upon me. They have parted my garments among them, and cast lots upon my vesture.

But remove not Thou Thy help far from me, O Lord; haste Thee to help me.

Deliver my soul from the sword; mine only begotten one from the hand of the dog.

Save me from the lion's mouth, and my lowliness from the horns of unicorns.

I will declare Thy Name unto my brethren; in the midst of the church will I sing praise unto Thee.

Ye that fear the Lord, praise Him; all ye the seed of Jacob, glorify Him.

Let all the seed of Israel fear Him.

For He hath not despised nor abhorred the supplication of the poor, neither hath He hid His face from me; but when I cried unto Him, He heard me.

My praise is of Thee in the great congregation; I will pay my vows before them that fear Him.

The poor shall eat and be satisfied, and they shall praise the Lord that seek Him; their hearts shall live for ever and ever.

All the ends of the earth shall remember and turn unto the Lord, and all the kindreds of the nations shall worship before Him.

For the kingdom is the Lord's, and He is the Governor among the nations.

All they that be fat upon earth have eaten and worshipped; all they that go down to the dust shall fall down before Him.

Yea, my soul liveth to Him, and my seed shall serve Him.

The generation that cometh shall be told of the Lord, and they shall declare His righteousness unto a people that shall be born, whom the Lord hath made.
