The heavens declare the glory of God, and the firmament showeth His handiwork.

Day unto day uttereth speech, and night unto night showeth knowledge.

There is no speech nor language, where their voices are not heard.

Their sound is gone out into all the earth, and their words to the ends of the world.

He hath set His tabernacle in the sun, and as a bridegroom coming out of his chamber,

He will rejoice as a giant to run his course. His going forth is from the end of heaven, and his circuit unto the end of it, and there is none that shall hide himself from the heat thereof.

The law of the Lord is blameless, converting souls; the testimony of the Lord is sure, giving wisdom to infants.

The statutes of the Lord are right, rejoicing the heart; the commandment of the Lord is bright, enlightening the eyes.

The fear of the Lord is clean, enduring for ever and ever; the judgments of the Lord are true, justified altogether.

More to be desired are they than gold, yea, than much precious stone; sweeter also than honey and the honeycomb.

For Thy servant keepeth them; in keeping of them there is great reward.

Who will understand transgressions? Cleanse Thou me from my secret faults, and from those of others spare Thy servant.

If they get not dominion over me, then shall I be blameless, and I shall be clear from great transgression.

And the words of my mouth shall be such as may please, and the meditation of my heart shall be always in Thy sight,

O Lord, my helper, and my redeemer.
