O Lord God of my salvation, I have cried day and night before Thee.

Let my prayer come before Thee; incline Thine ear unto my supplication.

For my soul is full of evils, and my life hath drawn nigh unto hell.

I am counted with them that go down into the pit; I am become as a man without help, free among the dead.

Like the bodies of the slain that sleep in the grave, whom Thou rememberest no more: and they are cut off from Thy hand.

They have laid me in the lowest pit, in darkness, and in the shadow of death.

Thy wrath is made strong over me, and Thou hast brought all Thy waves upon me.

Thou hast put away mine friends far from me; they have made me an abomination unto themselves.

I am delivered up, and I cannot come forth; mine eyes are grown weak from poverty.

Lord, I have called daily upon Thee, I have stretched out my hands unto Thee.

Wilt Thou work wonders for the dead? Or shall physicians raise them up to praise Thee?

Shall any in the grave tell of Thy mercy, and of Thy truth in that destruction?

Shall Thy wonders be known in that dark, and Thy righteousness in the land of that is forgotten?

But unto Thee have I cried, O Lord, and in the morning shall my prayer come before Thee.

Wherefore, O Lord, dost Thou cast off my soul, and turnest Thy face away from me?

A poor man am I, and in troubles from my youth; yea, having been exalted, I was humbled and brought low unto distress.

Thy fierce wrath hath passed upon me, and Thy terrors have troubled me.

They came round about me like water; all the day long they compassed me about together.

Friend and neighbour hast Thou put far from me, and mine acquaintance because of my misery.
