Let God arise, and let His enemies be scattered; let them also that hate Him flee before his face.

As smoke vanisheth, so let them vanish away; as wax melteth before the fire, so let the wicked perish at the presence of God.

But let the righteous be glad; let them rejoice before God; let them rejoice with gladness.

Sing unto God, sing praises to His name; prepare the way for Him that rideth upon the sunset. The Lord is His name; exult ye
before Him.

Let them be troubled at the presence of Him that is a father of the fatherless, and a judge of the widows; even God in his holy habitation.

God settleth the solitary in a house; He bringeth out with strength them that were imprisoned; yea, likewise them that embitter Him, that dwell in sepulchres.

O God, when Thou wentest forth before Thy people, when Thou didst pass through the wilderness,

The earth trembled, the heavens also dropped at the presence of the God of Sinai, at the presence of the God of Israel.

Thou, O God, shalt ordain for Thine inheritance a free rain; yea, it was weary, but Thou shalt restore it.

Thy creatures shall dwell therein; Thou, O God, hast prepared of Thy goodness for the poor.

The Lord shall give the word to them that preach good tidings with great power.

The king of the hosts of his beloved shall divide the spoils for the beauty of the house.

Though ye sleep among the lots, yet shall ye have the wings of a dove covered with silver, and her feathers with yellow gold.

When He that is in heaven appointeth kings over her, they shall be white as snow in Selmon.

The mountain of God is a rich mountain, a curdled mountain, a rich mountain.

Wherefore do ye suppose, ye curdled mountains? This is the mountain wherein God hath desired to dwell; yea, the Lord will dwell in it for ever.

The chariots of God are ten thousands, yea, thousands of them abounding; the Lord is among them in Sinai, in His holy place.

Thou hast ascended on high, Thou hast led captivity captive; Thou hast received gifts among men, yea, for they were rebellious, that Thou mightest dwell therein.

Blessed be the Lord, blessed be the Lord day by day; the God of our salvation shall prosper us along the way.

Our God is the God of salvation, and of the Lord, the Lord are the issues from death.

But God shall crush the heads of His enemies, the hairy crown of them that go on in their trespasses.

The Lord said, I will come again from Basan, I will come again in the depths of the sea,

That thy foot may be dipped in blood, the tongue of thy dogs in that of thine enemies.

Thy goings have been seen, O God, the goings of my God, of my king in His sanctuary.

The princes went before, and after them the singers, among the damsels playing with timbrels.

Bless ye God in the congregations, even the Lord from the fountains of Israel.

There is Benjamin the younger, in ecstasy, the princes of Juda their rulers, the princes of Zabulon, the princes of Nephthalim.

Command Thy strength, O God; strengthen, O God, that
which Thou hast wrought in us.

Because of Thy temple at Jerusalem shall kings bring presents unto Thee.

Rebuke the wild beasts of the reeds, the congregation of bulls among the heifers of the people, lest they exclude them that have been tried like silver. Scatter Thou the nations that delight in war.

Ambassadors shall come out of Egypt; Ethiopia shall soon stretch out her hands unto God.

Sing unto God, ye kingdoms of the earth; O sing praises unto the Lord, to Him that rideth upon the heaven of heavens to the dayspring. Lo, He will give to His voice a voice of power.

Ascribe glory unto God; His magnificence is over Israel, and His strength is in the clouds.

God is wonderful in His saints; the God of Israel is He that will give power and strength unto His people. Blessed be God.
