The Lord is God, to whom vengeance belongeth; the God of vengeance hath spoken freely.

Lift up Thyself, Thou that judgest the earth; render their reward to the proud.

Lord, how long shall the wicked, how long shall the wicked boast?

How long shall they utter and speak unrighteousness? How long shall all the workers of iniquity speak thus?

They have brought Thy people low, O Lord, and have hurt Thine inheritance.

They have slain the widow and the fatherless, and have murdered the stranger.

Yet they have said: The Lord shall not see, neither shall the God of Jacob regard it.

Understand, ye senseless among the people, and ye fools, at length be wise.

He that planted the ear, shall He not hear? Or He that formed the eye, shall He not see?

He that chastiseth the heathen, shall not He rebuke, He that teacheth man knowledge?

The Lord knoweth the thoughts of men, that they are vanity.

Blessed is the man whom Thou shalt chasten, O Lord, andt teach out of Thy law.

That Thou mayest give him rest from the days of adversity, until a pit be digged for the wicked.

For the Lord will not cast off His people, neither will He forsake His inheritance,

Until righteousness return unto judgment, and all the upright in heart are nigh unto it.

Who will rise up for me against the evildoers? or who will stand up with me against the workers of iniquity?

Unless the Lord had been my help, my soul had almost dwelt in Hell.

When I said: My foot hath slipped; Thy mercy, O Lord, brought me help.

According to the multitude of my sorrows in my heart, Thy comforts have given gladness to my soul.

Let not the throne of iniquity have fellowship with Thee, which frameth mischief in the name of the law.

They will hunt down the soul of the righteous, and condemn the innocent blood.

But the Lord is my refuge, and my God is the help of my hope.

And the Lord shall bring upon them their own iniquity, and according to their wickedness the Lord God shall cut them off.
