Unto Thee, O God, belongeth praise in Sion, and unto Thee shall a vow be rendered in Jerusalem.

Hearken unto my prayer, for unto Thee shall all flesh come.

The words of transgressors prevailed over us, but to our ungodliness Thou shalt be merciful.

Blessed is he whom Thou hast chosen and taken unto Thyself; he shall dwell in Thy courts.

We shall be satisfied with the goodness of Thy house; holy is Thy temple, wonderful in righteousness.

Hearken unto us, O God our Saviour, Thou hope of all the ends of the earth and those far off at sea.

Who by Thy strength settest fast the mountains, being girded about with power; 

Who troublest the depths of the sea; as for the roar its waves, who shall withstand them?

The nations shall be troubled, and they that dwell in the uttermost parts of the earth shall be afraid at Thy signs; Thou shalt make the outgoings of the morning and evening to rejoice.

Thou hast visited the earth and watered it plenteously; Thou hast greatly enriched it; the river of God is full of waters; Thou hast made ready their food, for so is its preparation.

Water its streams abundantly, increase its fruits; when they springeth up, they shall rejoice in its showers.

Thou shalt bless the crown of the year with Thy goodness, and Thy plains shall be filled with fatness.

The mountains of the wilderness shall be enriched, and the hills shall be girded about with joy.

The rams of the flock have clothed themselves with fleece, and the valleys shall abound with wheat; they shall cry aloud and shall sing.
