I will praise Thee, O Lord, with my whole heart; I will show forth all Thy marvellous works.

I will be glad and rejoice in Thee; I will sing praise to Thy Name, O Thou Most High.

When mine enemies are turned back, they shall be weakened, and perish before Thy face.

For Thou hast maintained my right and my cause; Thou hast sat on the throne, O Thou that judgest righteousness.

Thou hast rebuked the heathen, and the ungodly hath perished; Thou hast blotted out his Name for ever and ever.

The swords of the enemy have utterly failed, and his cities Thou hast destroyed.

His memorial hath perished with a resounding noise, but the Lord endureth for ever.

He hath prepared His throne for judgment, and He shall judge the world in righteousness; He shall minister judgment to the people in uprightness.

The Lord also is become a refuge for the poor, a seasonable help in times of trouble.

And let them that know Thy Name put their hope in Thee; for Thou, Lord, hast not forsaken them that seek Thee.

Sing praises to the Lord, which dwelleth in Sion; declare among the people His doings.

For He that maketh inquisition for blood hath remembered them; He hath not forgotten the cry of the poor.

Have mercy upon me, O God; consider my humiliation which I suffer of them that hate me, Thou that liftest me up from the gates of death:

That I may show forth all Thy praises in the gates of the daughter of Sion: we will rejoice in Thy salvation.

The heathen are stuck fast in the destruction that they have made; in the net which they hid is their own foot taken.

The Lord is known by the judgments which He executeth; the wicked is snared in the works of his own hands.

Let the wicked be turned away unto hades, all the nations that forget God.

For the needy shall not alway be forgotten; the patience of the poor shall not perish for ever.

Arise, O Lord, let not man prevail; let the heathen be judged in Thy sight.

O Lord, set a lawgiver over them; let the nations know themselves to be but men.

Why hast Thou stood afar off, O Lord? Why dost Thou despise us in times of trouble?

Whilst the wicked man is proud, the poor man burneth within; they are taken in the devices that they have imagined.

For the wicked praiseth himself for his heart’s desires, and the unrighteous blesseth himself therein.

The wicked hath provoked the Lord; in the multitude of his wrath he careth not; God is not in his sight.

His ways are always profane; Thy judgments are removed out of his sight; he will gain dominion over all his enemies.

For he hath said in his heart, I shall not be moved; from generation to generation I shall be without adversity.

His mouth is full of cursing and bitterness and fraud; under his tongue is toil and travail.

He sitteth in ambush with the rich in secret places, that he may slay the innocent; his eyes are set against the poor.

He lieth in wait secretly as a lion in his den; he lieth in wait to catch the poor, to catch the poor when he draweth him in to himself.

In his net will he humble himself; he will crouch and fall when he shall have power over the poor.

For he hath said in his heart, God hath forgotten; He hath turned away His face, that He may never see.

Arise, O Lord my God, let Thine hand be lifted up; forget not Thy poor to the end.

Wherefore hath the wicked provoked God? For he hath said in his heart, He will not require it.

Thou seest it, for Thou beholdest labour and wrath, to deliver him into Thy hands.

The poor hath been left unto Thee, for Thou art the helper of the fatherless.

Break Thou the arm of the wicked and the evil man; his sin shall be sought out, and shall be found no more.

The Lord is king for ever and ever; ye heathen shall perish out of His land.

Lord, Thou hast heard the desire of the poor; Thine ear hath been attentive to the preparation of their heart.

To judge for the fatherless, and for the humble; that man may no more presume to magnify himself upon earth.
