Thy hands have made me and fashioned me; give me understanding, and I shall learn Thy commandments.

They that fear Thee shall see me, and be glad, because I have hoped in Thy words.

I know, O Lord, that Thy judgments are right, and that with truth Thou hast humbled me.

Let Thy mercy now be for my comfort, according to Thy word unto Thy servant.

Let Thy tender mercies come unto me, and I shall live; for Thy law is my meditation.

Let the proud be ashamed, for they have transgressed against me unjustly; but I will meditate on Thy commandments.

Let those that fear Thee turn unto me, and those that know Thy testimonies.

Let my heart be blameless in Thy statutes, that I be not ashamed.

My soul fainteth for Thy salvation; I have hoped in Thy words.

Mine eyes have failed for Thy word, saying, When wilt Thou comfort me?

For I am become like a wineskin in the frost, yet have I not forgotten Thy statutes.

How many are the days of Thy servant? When wilt Thou execute judgment on them that persecute me?

Transgressors told me idle tales, but they are not after Thy law, O Lord.

All Thy commandments are truth; they persecuted me wrongfully, help Thou me.

They had almost made an end of me upon earth, but I forsook not Thy precepts.

Quicken me according to Thy mercy, and I shall keep the testimonies of Thy mouth.

For ever, O Lord, Thy word endureth in heaven.

Thy truth is unto generation and generation; Thou hast established the earth, and it abideth.

The day continueth according to Thine ordinance, for all things are Thy servants.

If Thy law had not been my meditation, I should have perished in my humiliation.

I will never forget Thy precepts, for by them Thou hast quickened me.
