I will exalt Thee, O God my King, and I will bless Thy Name for ever, yea, for ever and ever.

Every day will I bless Thee, and I will praise Thy Name for ever, yea, for ever and ever.

Great is the Lord, and exceedingly to be praised, and of His majesty there is no end.

Generation after generation shall praise Thy works, and Thy might shall they declare.

They shall speak of the magnificence of the glory of Thy holiness, and shall tell of Thy wondrous works.

And they shall speak of the might of Thy fearsome acts, and shall tell of Thy majesty.

They shall overflow at the memory of the abundance of Thy goodness, and shall rejoice exceedingly in Thy righteousness.

Compassion and merciful is the Lord, long-suffering and plenteous in mercy.

The Lord is good unto all, and His tender mercies are over all His works.

Let all Thy works praise Thee, O Lord, and let Thy saints bless Thee.

They shall speak of the glory of Thy kingdom, and tell of Thy power,

To make known to the sons of men Thy power, and the glorious majesty of Thy kingdom.

Thy kingdom is an everlasting kingdom, and Thy dominion is in every generation and generation.

Faithful is the Lord in all His words, and holy in all His works.

The Lord upholdeth all that fall, and raiseth up all those that be bowed down.
 
The eyes of all look to Thee in hope, and Thou givest them their food in due season.

Thou openest Thy hand, and fillest every living thing with Thy favour.

Righteous is the Lord in all His ways, and holy in all His works.

The Lord is nigh unto all them that call upon Him, to all that call upon Him in truth.

He will fulfil the desire of them that fear Him; He will hear their prayer and save them.

The Lord preserveth all them that love Him, but all the sinners shall He utterly destroy.

My mouth shall speak praise of the Lord, and let all flesh bless His holy Name for ever, yea, for ever and ever.
