I will sing of Thy mercies, O Lord, for ever; with my mouth will I show forth Thy truth to generation and generation.

For Thou hast said, Mercy shall be built up for ever; Thy truth shall be established in the heavens.

I have made a covenant with My chosen, I have sworn unto David My servant.

Thy seed will I establish for ever, and build up thy throne to generation and generation.

The heavens shall praise Thy wonders, O Lord, Thy truth alsoin the congregation of the saints.

For who in the heaven can be compared unto the Lord? and who among the sons of God can be likened unto the Lord?

God who is glorified in the assembly of the saints, great and terrible toward all them that are round about Him.

O Lord God of hosts, who is like unto Thee? Thou art mighty, O Lord, and Thy truth is round about Thee.

Thou art ruler over the strength of the sea, and Thou stillest the tumult of her waves.

Thou hast humbled the proud, as one that is slain; and Thou hast scattered Thine enemies with Thy strong arm.

The heavens are Thine, the earth also is Thine; as for the world and the fulness thereof, Thou hast founded them.

The north and the sea Thou hast created them; Tabor and Hermon shall rejoice in Thy Name.

Thine is the mighty arm. Let Thy hand be strengthened, let Thy right hand be exalted.

Justice and judgment are the preparation of Thy throne; mercy and truth shall go before Thy face. Blessed is the people that knoweth the joyful sound.

They shall walk, O Lord, in the light of Thy countenance, and in Thy Name shall they rejoice all the day, and in Thy righteousness shall they be exalted.

For Thou art the glory of their strength, and in Thy favour our horn shall be exalted.

For of the Lord is our defence, and of the Holy One of Israel, our King.

Then Thou spakest in vision to Thy sons, and saidst, I have laid help upon one that is mighty, I have exalted one chosen out of My people.

I have found David My servant, with My holy oil have I anointed him.

For My hand shall support him, Mine arm also shall strengthen him. His enemy shall have no advantage over him, nor shall the son of wickedness have power to hurt him more.

And I will cut down his foes before his face, and put them that hate him to flight.

And My truth and My mercy shall be with him, and in My Name shall his horn be exalted.

I will set his hand also in the sea, and his right hand in the rivers.

He shall cry unto Me, and say: Thou art my Father, my God, and the helper of my salvation.

And I will make him My first born, higher than the kings of the earth.

My mercy will I keep for him for evermore, and My covenant shall stand fast with him.

And I will establish his seed unto ages of ages, and his throne shall be as the days of heaven.

If his children forsake My law, and walk not in My judgments;

If they profane My statutes, and keep not My commandments;

Then will I visit their transgressions with a rod, and their iniquities with stripes.

Nevertheless My mercy will I not utterly take from them, nor wrong them in My truth.

Neither will I profane My covenant, nor make void the things that go out of My lips.

Once have I sworn by My holiness, that I will not lie unto David.

His seed shall endure for ever, and his throne as the sun before Me, and as the moon that is established for ever, and as a faithful witness in heaven.

But Thou hast cast off and brought to nought; Thou hast been wroth with Thine anointed.

Thou hast destroyed the covenant of Thy servant; Thou hast profaned his sanctuary to the ground.

Thou hast broken down all his hedges; Thou hast made his stronghold a terror.

All that pass by the way have spoiled him; he is become a reproach to his neighbours.

Thou hast set up the right hand of them that afflict him, Thou hast made all his enemies to rejoice.

Thou hast turned the help of his sword, and hast not holpen him in battle.

Thou hast made an end of his purification; Thou hast cast his throne down to the ground.

The days of his time hast Thou shortened;  Thou hast covered him with shame.

How long, O Lord? wilt Thou hide Thyself for ever? shall Thy wrath burn like fire?

Remember what my substance is. For hast Thou created all the sons of man in vain?

What man is he that liveth, and shall not see death? Shall he deliver his soul out of the hand of hades?

Lord, where are Thine ancient mercies, which Thou swarest unto David in Thy truth?

Remember, Lord, the reproach of Thy servants, which I have endured in my bosom of many nations.

Wherewith Thine enemies have reproached, O Lord, wherewith they have reproached the reward of Thine anointed.

Blessed be the Lord for evermore. So be it. So be it.
