O give thanks to the Lord, and call upon His Name; make known His deeds among the nations.

Sing unto Him, sing psalms unto Him; tell of all His wondrous works.

Glory in His holy Name; let the heart of them rejoice that seek the Lord.

Seek the Lord, and be strengthened; seek His face at all times.

Remember His marvellous works that He hath done; His wonders, and the judgments of His mouth.

O ye seed of Abraham His servant, ye children of Jacob His chosen.

He is the Lord our God; His judgments are in all the earth.

He hath remembered His covenant for ever, the word which He commanded to a thousand generations;

Which He made with Abraham, and His oath unto Isaac.

And confirmed the same unto Jacob for a law, and to Israel for an everlasting covenant.

Saying, Unto thee will I give the land of Chanaan, the lot of your inheritance.

When they were but a few men in number, very few, and strangers in it.

And they went from one nation to another, from one kingdom to another people.

He suffered no man to do them wrong; yea, He reproved kings for their sake;

Saying, Touch not Mine anointed, and do My prophets no harm.

Moreover He called for a famine upon the land; He brake the whole staff of bread.

He sent a man before them, even Joseph, who was sold for a slave.

Whose feet they humbled with fetters; his life was spent in irons, until his word came to pass.

The word of the Lord tried him, the king sent and loosed him, even the ruler of the people, and let him go free.

He made him lord of his house, and ruler of all his substance;

To instruct his princes as himself, and teach his elders wisdom.

Israel also came into Egypt, and Jacob sojourned in the land of Cham.

And He increased His people greatly, and made them stronger than their enemies.

He turned their heart to hate His people, and to deal subtilly with His servants.

He sent Moses His servant, and Aaron whom He had chosen.

He established His signs among them, and His wonders in the land of Cham.

He sent darkness, and made it dark; for they were embittered against His words.

He turned their waters into blood, and slew their fish.

Their land brought forth frogs in abundance, in the inner chambers of their kings.

He spake, and the dog fly came, and gnats in all their coasts.

He gave them hail for rain, and flaming fire in their land.

He smote their vines also and their fig trees, and brake all the trees of their coasts.

He spake, and the locust came, and caterpillars, and that without number,

And did eat up all the herbs in their land, and devoured all the fruit of their land.

He smote also all the firstborn in their land; the first fruits of all their labour.

He brought them forth also with silver and gold, and there was not one feeble person among their tribes.

Egypt was glad when they departed, for the fear of them fell upon them.

He spread a cloud for a covering for them, and fire to give them light in the night.

They asked, and the quail came; and He satisfied them with the bread of heaven.

He opened the rock, and the waters gushed out; the rivers ran in dry places.

For He remembered His holy promise, which He had spoken unto Abraham His servant.

And He brought forth His people with joy, and His chosen with gladness.

And gave them the lands of the heathen, and they inherited the labour of the people.

That they might observe His statutes, and seek His law.
