I will love Thee, O Lord, my strength. The Lord is my rock, and my refuge, and my deliverer.

My God is my helper, and in Him will I hope; my defender, and the horn of my salvation, and my helper.

I will call upon the Name of the Lord with praise, and I shall be saved from mine enemies.

The sorrows of death compassed me, and the floods of iniquity sore troubled me.

The sorrows of hell compassed me about; the snares of death prevented me.

And in mine affliction I called upon the Lord, and cried unto my God.

He heard my voice out of His holy temple, and my cry before Him shall come into His ears.

And the earth shook and trembled, the foundations also of the mountains were troubled and shaken, because God was wroth with them.

There went up a smoke in His wrath, and fire from His countenance set all aflame; coals were kindled by it.

He bowed the heavens also, and came down, and thick darkness was under His feet.

And He ascended upon the cherubim, and did fly; yea, He did fly upon the wings of the wind.

And He made darkness His secret place, His pavilion round about Him, dark water in the clouds of the air.

At the brightness that was before Him the clouds passed, hailstones and coals of fire.

The Lord also thundered from the heavens, and the Highest gave His voice.

Yea, He sent out His arrows, and scattered them; and He multiplied lightnings, and discomfited them.

And the springs of waters were seen, and the foundations of the world were discovered, at Thy rebuke, O Lord, at the breath of the spirit of Thy wrath.

He sent from on high, and took me; He received me out of many waters.

He will deliver me from my mighty enemies, and from them that hate me, for they are stronger than I.

They prevented me in the day of my trouble, but the Lord was my stay.

He brought me forth also into a large place; He will deliver me, because He delighted in me.

And the Lord will reward me according to my righteousness, and according to the cleanness of my hands will He recompense me.

For I have kept the ways of the Lord, and have not done wickedly toward my God.

For all His judgments are before me, and His statutes have not departed from me.

And I will be blameless with Him, and will keep myself from mine iniquity.

And the Lord will reward me according to my righteousness, and according to the cleanness of my hands in His eyesight.

With the holy Thou wilt be holy, and with the innocent man Thou wilt be innocent; and with the elect Thou wilt be elect, and with the perverse Thou wilt deal perversely.

For Thou wilt save the humble people, and bring down the eyes of the proud.

For Thou wilt light my lamp, O Lord my God; Thou wilt enlighten my darkness.

For by Thee shall I be delivered from a troop of thieves, and by my God shall I leap over a wall.

As for my God, His way is blameless; the words of the Lord are tried in the fire; He is the defender of all those that hope in Him.

For who is God save the Lord? And who is God save our God?

It is God that hath girded me with strength, and made my way blameless.

That maketh my feet like hind’s feet, and setteth me upon high places.

He teacheth my hands to war; and Thou hast made mine arms as a brazen bow.

Thou hast also given me the shield of salvation, and Thy right hand hath holden me up.

And Thine instruction hath corrected me unto the end; Thine instruction it is that shall teach me.

Thou hast enlarged my steps under me, and my footsteps are not weakened.

I will pursue mine enemies, and overtake them; neither shall I turn again until they be consumed.

I will afflict them, and they shall not be able to rise; they shall fall under my feet.

For Thou hast girded me with strength unto the battle; Thou hast subdued under me them that rose up against me.

Thou hast also made mine enemies turn their backs before me, and hast destroyed them that hated me.

They cried, but there was none to save them; even unto the Lord, but He heard them not.

And I will beat them small as the dust before the face of the wind; I will trample them down as the dirt in the streets.

Deliver me from the strivings of the people; Thou shalt make the head of the heathen.

A people whom I have not known have served me; at the hearing of the ear they obeyed me.

The children of strangers lied unto me, the children of strangers waxed old, and halted from their paths.

The Lord liveth, and blessed be my God, and let the God of my salvation be exalted.

It is God that avengeth me, and hath subdued the people under me; my deliverer from mine angry enemies.

Thou wilt lift me up above those that rise up against me; deliver me from the unrighteous man.

Therefore will I give thanks unto Thee, O Lord, among the heathen, and sing praises unto Thy Name.

He magnifieth the salvation of His king, and worketh mercy for David His anointed, and for his seed for evermore.
