Bow down Thine ear, O Lord, and hear me, for I am poor and needy.

Preserve my soul, for I am holy; O Thou my God, save Thy servant that hopeth in Thee.

Be merciful unto me, O Lord, for unto Thee will I cry all the day long.

Rejoice the soul of Thy servant, for unto Thee have I lifted up my soul.

For Thou, Lord, art good and gentle, and plenteous in mercy unto all them that call upon Thee.

Give ear, O Lord, unto my prayer, and attend to the voice of my supplication.

In the day of my trouble have I cried unto Thee, for Thou hast heard me.

Among the gods there is none like unto Thee, O Lord, neither are there any works like unto Thy works.

All nations whom Thou hast made shall come and worship before Thee, O Lord, and shall glorify Thy name.

For Thou art great, and doest wondrous things, Thou art God alone.

Lead me in Thy way, O Lord, and I will walk in Thy truth; let my heart rejoice that I may fear Thy name.

I will praise Thee, O Lord my God, with all my heart, and I will glorify Thy name for evermore.

For great is Thy mercy toward me, and Thou hast delivered my soul from the lowest hell.

O God, transgressors are risen against me, and the assembly of the mighty hath sought after my soul, and have not set Thee before them.

But Thou, O Lord my God, art full of compassion, and merciful, long-suffering, and plenteous in mercy, and true.

Look Thou upon me, and have mercy upon me; give Thy strength unto Thy servant, and save the son of Thine handmaid.

Work in me a token for good, and let them which hate me see, and be ashamed; because Thou, Lord, hast holpen me, and comforted me.
