O Lord, rebuke me not in Thy wrath, neither chasten me in Thy hot displeasure.

For Thine arrows are stuck fast in me, and Thou hast pressed Thine hand heavily upon me.

There is no soundness in my flesh because of Thine anger, neither is there any peace in my bones because of my sins.

For mine iniquities are gone over my head; as a heavy burden have they pressed sore upon me.

My wounds stink and are corrupt, because of my foolishness.

I am troubled and bowed down greatly; I went with mourning countenance all the day long.

For my loins are filled with mockings, and there is no healing in my flesh.

I am troubled and brought down greatly; I have roared by reason of the groaning of my heart.

Lord, all my desire is before Thee, and my groaning is not hid from Thee.

My heart is troubled, my strength hath failed me; as for the light of mine eyes, it also is gone from me.

My friends and my neighbours drew near and stood over against me, and my kinsmen stood afar off.

They also that sought after my life used violence, and they that sought my hurt spake vanities, and imagined deceits all the day long.

But I, as a deaf man, heard not; and I was as a dumb man that openeth not his mouth.

And I was as a man that heareth not, and in whose mouth are no reproofs.

For in Thee, O Lord, have I hoped; Thou wilt hear me, O Lord my God.

For I said, Let never mine enemies rejoice over me; for when my feet slipped, they made boast against me.

For I am ready for scourges, and my sorrow is continually before me.

For I will declare mine iniquity, and be sorry for my sin.

But mine enemies live, and are stronger than I, and they that hated me wrongfully are multiplied.

They that render me evils for good have slandered me, because I followed the thing that good is.

Forsake me not, O Lord my God; depart not from me.

Make haste to help me, O Lord of my salvation.
