O God, who shall be likened unto Thee? Hold not Thy peace, and be not still, O God.

For lo, Thine enemies have made a tumult, and they that hate Thee have lifted up the head.

They have taken wicked counsel against Thy people, and consulted against Thy saints.

They have said, Come, let us cut them off, that they be no more a nation, and let the name of Israel be no more in remembrance.

For they have consulted together with one consent; they have made a covenant against Thee, the tents of the Idumeans and the Ismaelites,

Moab and the Hagarenes, Gebal and Ammon and Amalek, and the strangers, with them that dwell at Tyre. Assur also is come with them; they have holpen the children of Lot.

Do unto them as Thou didst unto Madiam and Sisara, as to Jabin at the brook of Kisson.

They were destroyed at Endor, they became as dung for the earth.

Make their princes like Oreb and Zeb, and Zebee and Salmana, yea, all their princes who said, Let us take to ourselves the sanctuary of God for an inheritance.

O my God, make them like a wheel, as the stubble before the face of the wind,

As the fire that shall burn the wood, as the flame that shall consume the mountains.

So shalt Thou pursue them with Thy tempest, and trouble them in Thy wrath.

Fill their faces with dishonour, and they shall seek Thy Name, O Lord.

Let them be ashamed and troubled for ever and ever, and let them be confounded and destroyed.

And let them know that the Lord is Thy Name; Thou alone art the Most High over all the earth.
