O Lord my God, in thee have I put my hope; save me from all them that persecute me, and deliver me.

Lest he seize my soul like a lion, while there is none to deliver or to save.

O Lord my God, if I have done this; if there be iniquity in my hands;

If I have rewarded evils unto them that rewarded me evils, then let me fall empty from mine enemies.

Let the enemy persecute my soul, and take it; yea, let him tread down my life upon the earth, and lay my glory in the dust.

Arise, O Lord, in thine anger; lift up thyself in the uttermost borders of thine enemies.

And awake, O Lord my God, in the commandment that Thou hast commanded, and a congregation of the people shall compass Thee about. For their sakes therefore return Thou on high.

The Lord shall judge the people. Judge me, O Lord, according to my righteousness, and according to mine innocence that is in me.

Let the wickedness of the wicked come to an end, but direct thou the just, O God, that searchest the hearts and reins.

Righteous is my help from God, which saveth the upright in heart.

God is a righteous judge, strong and forbearing, and inflicteth not anger every day.

If ye turn not, He will furbish his sword; He hath bent his bow, and made it ready.

And He hath prepared on it the instruments of death; He hath ordained His arrows for them that burn.

Behold, he hath travailed with iniquity; he hath conceived toil, and brought forth wickedness.

He opened a pit, and digged it, and shall fall into the ditch which he himself made.

His travail shall return upon his own head, and his unrighteousness shall come down upon his own pate.

I will praise the Lord according to His righteousness, and will sing praise to the name of the Lord Most High.
