Blessed be the Lord my God, who teacheth my hands to battle, and my fingers to fight.

My mercy, and my refuge; my help, and my deliverer.

My defender, in whom I have hoped; who hath subdued my people under me.

Lord, what is man, that Thou art made known unto him? or the son of man, that Thou makest account of him?

Man is like to vanity; his days as a shadow pass away.

Bow the heavens, O Lord, and come down; touch the
mountains, and they shall smoke.

Cast forth lightning, and Thou shalt scatter them; send out Thine arrows, and Thou shalt trouble them.

Send Thine hand from above; rid me, and deliver me out of great waters, from the hand of strange children,

Whose mouth hath spoken vanity, and their right hand is the right hand of iniquity.

I will sing a new song unto Thee, O God; upon a psaltery of ten strings will I sing praises unto Thee;

Who givest salvation unto kings; who deliverest David Thy servant from the evil sword.

Rid me, and deliver me from the hand of strange children, whose mouth hath spoken vanity, and their right hand is the right hand of iniquity.

Whose sons are like new plants, strongly planted in their youth; their daughters decked out, adorned after the fashion of a temple.

Their garners full, flowing out with all manner of store;

Their sheep fruitful with young abounding in their gateways; their oxen fat.

There is no breach of wall or passage, neither any crying in their streets.

They have called the people blessed that is in such a case; but blessed is that people whose God is the Lord.
