Lord, remember David and all his meekness,

How he made an oath unto the Lord, and vowed unto the God of Jacob.

I will not go into the tabernacle of my house; I will not go up into the couch of my bed;

I will not give sleep to mine eyes, nor slumber to mine eyelids, nor rest to my temples,

Until I find out a place for the Lord, an habitation for the God of Jacob.

Behold, we heard it in Ephratha; we found it in the fields of the wood.

Let us go into His tabernacles; let us worship at the place where His feet have stood.

Arise, O Lord, into Thy rest; Thou, and the ark of Thy holiness.

Thy priests shall be clothed with righteousness, and Thy saints shall rejoice.

For Thy servant David's sake turn not away Thy face from Thine anointed.

The Lord hath sworn in truth unto David, and He will not annul it,

Of the fruit of thy body will I set upon thy throne,

If thy children will keep My covenant and these testimonies which I shall teach them,

Their children shall also sit upon thy throne for evermore.

For the Lord hath chosen Sion, He hath chosen it for His habitation.

This is my rest for ever and ever; here will I dwell, for I have chosen it.

I will abundantly bless her provision, I will satisfy her poor with bread.

I will clothe her priests with salvation, and her saints shall rejoice with joy.

There will I make to spring forth a horn for David; I have ordained a lamp for Mine anointed.

His enemies will I clothe with shame, but upon himself shall My holiness flourish.
