The Lord is my light and my saviour; whom shall I fear? The Lord is the defender of my life; of whom shall I be afraid?

When the wicked came upon me to eat up my flesh, even them that afflict me and are mine enemies, they were weakened, and fell.

Though a host should encamp itself against me, my heart shall not be afraid; though war should rise against me, in this have I hoped.

One thing I have asked of the Lord, this will I seek after: that I may dwell in the house of the Lord all the days of my life, that I may behold the delight of the Lord, and that I may visit His holy temple.

For in the day of my troubles He hid me in His tabernacle; He sheltered me in the secret place of His tabernacle; He set me up upon a rock.

And now, behold, He hath lifted up my head above mine enemies; I went round about and offered in His tabernacle a sacrifice of praise and joy; I will sing and chant unto the Lord.

Hearken unto my voice, O Lord, with which I have cried to thee; have mercy upon me and hearken unto me.

My heart hath said unto Thee, I will seek the Lord. My face hath sought Thee; Thy face, O Lord, will I seek.

Turn not away Thy face from me, and turn not away in anger from Thy servant.

Be Thou my help, cast me not away; neither forsake me, O God my Saviour.

For my father and my mother have forsaken me, but the Lord hath taken me to Himself.

Teach me Thy way, O Lord, and lead me in the right path on account of mine enemies.

Deliver me not over to the souls of those that afflict me; for unjust witnesses are risen up against me, and injustice hath deceived itself.

I believe that I shall see the goodness of the Lord in the land of the living.

Wait on the Lord; be of good courage, and let thy heart be strengthened, and wait on the Lord.
