Give ear, O God, unto my prayer, and despise not my supplication; attend unto me, and hear me.

I was grieved in my meditation, and was troubled, because of the voice of the enemy, and the oppression of the sinner.

For they brought iniquity upon me, and in wrath were they angry against me.

My heart is troubled within me, and the terror of death is fallen upon me.

Fearfulness and trembling are come upon me, and darkness hath covered me.

And I said, Who will give me wings like a dove? And I will fly, and be at rest.

Lo, I fled far off, and dwelt in the wilderness.

I waited for God that saveth me from faintheartedness, and from tempest.

Plunge them into the depths, O Lord, and divide their tongues, for I have seen iniquity and strife in the city.

Day and night they go round about it upon the walls; iniquity and toil and unrighteousness are in the midst of it.

And usury and deceit are not departed from its streets.

For if an enemy had reproached me, then I might have endured it; and if he that hateth me had magnified his words against me, then I would have hid myself from him.

But thou it was, a man of like mind, my guide and my familiar friend.

Who didst sweeten my meals together with me; in the house of God we walked in oneness of mind.

Let death come upon such ones, and let them go down alive into hell; for wickedness is in their dwellings, and in the midst of them.

As for me, I cried unto God, and the Lord heard me.

Evening, and morning, and noonday will I declare and tell of it; and He shall hear my voice.

He shall redeem my soul in peace from them that draw nigh unto me; for they among many were with me.

God shall hear, and He shall humble them, even He that abideth of old.

For there is no change with them, and they have not feared God.

He hath put forth His hand to repay; they have defiled His covenant.

They were scattered by the wrath of His countenance, and their hearts have drawn nigh. Their words were smoother than oil, and yet are they darts.

Cast thy care upon the Lord, and He shall nourish thee; He shall never suffer the righteous to be moved.

But Thou, O God, shalt bring those men down into the pit of destruction. Bloody and deceitful men shall not live out half their days; but, O Lord, I will hope in Thee.
