Hearken unto my righteousness, O Lord; attend unto my supplication. Give ear unto my prayer, that goeth not out of feigned lips.

Let my judgment come forth from Thy presence; let mine eyes behold the things that are right.

Thou hast proved mine heart, Thou hast visited it in the night; Thou hast tried me by fire, and unrighteousness hath not been found in me.

That my mouth may not speak the works of men, for the sake of the words of Thy lips have I kept hard ways.

Perfect Thou my goings in Thy paths, that my footsteps may not be moved.

I have cried, for Thou hast heard me, O God; incline Thine ear unto me, and hear my words.

Let Thy mercies be made marvellous, O Thou that savest them who put their trust in Thee. From them that have resisted Thy right hand, keep me, O Lord, as the apple of Thine eye.

Thou wilt shelter me with the shelter of Thy wings, from the face of the ungodly, who have afflicted me.

Mine enemies have compassed my soul; they have enclosed themselves in their own fat, with their mouth hath they spoken pride.

They have cast me forth, and have now compassed me about; they have set their eyes bowing down to the earth.

They have taken me, like as a lion that is ready for his prey, and as it were a young lion lurking in secret places.

Arise, O Lord, prevent and overtake them; deliver my soul from the wicked, Thy sword from the enemies of Thy hand.

O Lord, from Thy few do Thou separate them from the earth in their life; yea, of those things which Thou hath hidden, their belly was filled.

They have satisfied themselves with that which belongeth unto swine, and to their infants have they left the remnants.

But as for me, I shall appear before Thy face in righteousness; I shall be satisfied when Thy glory shall appear to me.
