I will bless the Lord at all times; His praise shall continually be in my mouth.

My soul shall be praised in the Lord; let the meek hear thereof, and be glad.

O magnify the Lord with me, and let us exalt His Name for ever.

I sought the Lord, and He heard me, and delivered me from all my troubles.

Come unto him, and be lightened; and your faces shall not be ashamed.

This poor man cried, and the Lord heard him, and saved him out of all his troubles.

The angel of the Lord shall encamp round about them that fear Him, and shall deliver them.

O taste and see that the Lord is good; blessed is the man that hopeth in Him.

O fear the Lord, all ye His saints; for there is no want to them that fear Him.

The rich became poor, and suffered hunger; but they that seek the Lord shall not be deprived of any good thing.

Come, ye children, hearken unto me; I will teach you the fear of the Lord.

What man is he that desireth life, that loveth to see good days?

Keep thy tongue from evil, and thy lips from speaking guile.

Turn away from evil, and do good; seek peace, and pursue it.

The eyes of the Lord are upon the righteous, and His ears are open unto their supplication.

The face of the Lord is against them that do evil, to cut off the remembrance of them from the earth.

The righteous cried, and the Lord heard them, and delivered them out of all their troubles.

The Lord is nigh unto them that are of a contrite heart, and will save such as be of an humble spirit.

Many are the afflictions of the righteous, but the Lord shall deliver them out of them all.

The Lord keepeth all their bones; not one of them shall be broken.

The death of the sinners is evil, and they that hate the righteous shall go astray.

The Lord shall redeem the souls of His servants, and none of them that hope in Him shall go astray.
