I am Thine, save me; for I have sought Thy precepts.

The wicked have waited for me to destroy me, but I have understood Thy testimonies.

I have seen an end of all perfection, but Thy commandment is exceeding broad.

O how have I loved Thy law, O Lord! It is my meditation all the day.

Thou through Thy commandment hast made me wiser than mine enemies, for it is mine for ever.

I had more understanding than all my teachers, for Thy testimonies are my meditation.

I had more understanding than mine elders, because I sought Thy commandments.

I have refrained my feet from every evil way, that I might keep Thy words.

I have not departed from Thy judgments, for Thou hast appointed a law for me.

How sweet are Thy words unto my throat! yea, sweeter than honey to my mouth.

Through Thy commandments have I gained understanding; therefore have I hated every unrighteous way.

Thy law is a lamp unto my feet, and a light unto my paths.

I have sworn, and am steadfastly purposed, that I will keep the judgments of Thy righteousness.

I have been humbled exceedingly; quicken me, O Lord, according unto Thy word.

Be pleased with the freewill offerings of my mouth, O Lord, and teach me Thy judgments.

My soul is continually in Thy hand, yet have I not forgotten Thy law.

Sinners have laid a snare for me, yet I erred not from Thy precepts.

Thy testimonies have I taken as an heritage for ever, for they are the rejoicing of my heart.

I have inclined my heart to perform Thy statutes for ever, for a recompense.

I have hated transgressors, but Thy law have I loved.

Thou art my helper and defender; I have hoped in Thy words.

Depart from me, ye evil doers, and I will search the commandments of my God.

Uphold me according unto Thy word, and quicken me; and turn me not away in shame from mine expectation.

Help me, and I shall be saved, and I will meditate in Thy statutes always.

Thou hast despised all them that departed from Thy statutes, for their inward thought is unrighteous.

I have accounted as transgressors all the sinners of the earth; therefore have I loved Thy testimonies.

Nail down my flesh with the fear of Thee, for I am afraid of Thy judgments.

I have done judgment and justice; give me not over unto them that wrong me.

Receive Thy servant unto good; let not the proud accuse me falsely.

My eyes have failed for Thy salvation, and for the word of Thy righteousness.

Deal with Thy servant according unto Thy mercy, and teach me Thy statutes.

I am Thy servant; give me understanding, and I shall know Thy testimonies.

It is time for the Lord to act, for they have made void Thy law.

Therefore have I loved Thy commandments above gold and topaz.

Therefore have I directed myself according to all Thy commandments; I have hated every unrighteous way.

Thy testimonies are wonderful; therefore hath my soul sought them.

The unfolding of Thy words shall give light and understanding unto the simple.

I opened my mouth, and drew in my breath; for I longed for Thy commandments.
