Give ear, O shepherd of Israel, Thou that leadest Joseph like a sheep.

Thou that sittest upon the cherubim, show Thyself before Ephraim, Benjamin and Manasses.

Stir up Thy strength, and come to save us.

Turn us again, O God, and cause Thy face to shine, and we shall be saved.

O Lord God of hosts, how long wilt Thou be angry against the prayer of Thy servants?

Wilt Thou feed us with the bread of tears, and give us tears to drink in great measure?

Thou hast made us a strife among our neighbours, and our enemies have scoffed at us.

Turn us again, O Lord of hosts, and cause Thy face to shine, and we shall be saved.

Thou hast brought a vine out of Egypt; Thou hast cast out the heathen, and planted it.

Thou preparedst the way before it, and Thou plantedst the roots thereof, and it filled the earth.

The shadows thereof covered the mountains, and the boughs thereof the cedars of God.

It stretched forth its shoots unto the sea, and its branches unto the rivers.

Why hast Thou broken down its hedge, and all they that pass by the way do pluck the fruit?

The boar out of the wood hath wasted it, and the wild beast hath devoured it.

Turn again, O God of hosts; and look down from heaven, and behold, and visit this vine.

And perfect that which Thy right hand hath planted, and look upon the son of man, whom Thou hast made strong for Thyself.

It is burned with fire, and dug up; they shall perish at the rebuke of Thy face.

Let Thy hand be upon the man of Thy right hand, and upon the son of man whom Thou hast made strong for Thyself.

And we will not depart from Thee; Thou shalt quicken us, and we will call upon Thy Name.

Turn us again, O Lord God of hosts; and cause Thy face to shine, and we shall be saved.
