O Lord, Thou hast proved me, and Thou knowest me. Thou knowest my downsitting and mine uprising; Thou hast understood my thoughts afar off.

Thou hast searched out my path and my lot, and hast foreseen all my ways; for there is no guile upon my tongue.

Behold, O Lord, Thou knowest all things, the last and the first; Thou hast fashioned me, and laid Thy hand upon me.

Thy knowledge is too wonderful for me; it is great, I cannot attain unto it.

Whither shall I go from Thy Spirit? and whither shall I flee from Thy presence?

If I ascend up into heaven, Thou art there; if I go down into hades, Thou art there present.

If I take up my wings to the morning, and dwell in the uttermost parts of the sea, even there shall Thy hand lead me, and Thy right hand shall hold me.

And I said: Surely the darkness shall cover me, and in my pleasure shall the night be turned to day.

For darkness will not be darkness with Thee, but night shall be bright as day; as is the darkness, even so shall be the light thereof.

For Thou hast possessed my reins; Thou hast holpen me, O Lord, from my mother's womb.

I will give Thee thanks, for Thou art wondrous and fearful; marvellous are Thy works, and my soul knoweth it well.

My bones are not hid from Thee, which Thou hast made in secret; nor my substance in the lowest parts of the earth.

Thine eyes did see my substance, yet being imperfect; and in Thy book shall all mankind be written; daily are they fashioned, when as yet there be none of them.

How honoured also are Thy friends unto me, O Lord! their rule is greatly strengthened.

I will number them, and they shall be multiplied in number more than the sand; when I awake, I am still with Thee.

Surely Thou wilt slay the wicked, O God! Depart from me, ye bloody men. For Thou shalt say of their thought: They shall take Thy cities in vain.

Have not I hated them, O Lord, that hate Thee? and have I not pined away because of Thine enemies?

I have hated them with a perfect hatred, and they are counted mine enemies.

Prove me, O Lord, and know my heart; try me, and know my ways.

And see if there be any wicked way in me, and lead me in the way everlasting.
