The God of gods, even the Lord, hath spoken, and called the earth from the rising of the sun unto the going down thereof.

Out of Sion is the magnificence of His beauty.

God our God shall come visibly, and shall not keep silence.

A fire shall blaze before Him, and a mighty tempest shall be round about Him.

He shall call to the heavens above; and to the earth, that He may judge His people.

Gather His saints together unto Him, those that have established His covenant upon sacrifices.

And the heavens shall declare His righteousness; for God Himself is judge.

Hear, O My people, and I will speak to thee, O Israel; and I will testify against thee; I am God, even Thy God.

I will not reprove thee for sacrifices, for thy burnt offerings are continually before Me.

I will not welcome bullocks out of thy house, nor he-goats out of thy flocks.

For all the beasts of the field are Mine, the cattle upon the mountains, and the oxen.

I know all the fowls of the air, and the beauty of the fields is
Mine.

If I were hungry, I would not tell thee, for the world is Mine, and all the fulness thereof.

Will I eat the flesh of bulls, or drink the blood of goats?

Offer unto God a sacrifice of thanksgiving, and pay thy vows unto the Most High.

And call upon Me in the day of thy trouble, and I will deliver thee; and thou shalt glorify Me.

But unto the wicked God hath said, Why dost thou declare Mine ordinances, and takest My covenant in thy mouth?

Thou hast hated instruction, and hast cast My words behind thee.

When thou sawest a thief, then thou didst run with him; and thou hast been partaker with the adulterer.

Thy mouth hath multiplied evil, and thy tongue hath framed deceits.

Thou satest and spakest against thy brother, and laidst a scandal against thy mother's son.

These things hast thou done, and I kept silence. Thou thoughtest wickedly that I should be like thee; but I will reprove thee, and set thy sins before thine eyes.

Now consider this, ye that forget God, lest He snatch you away, and there be none to deliver.

A sacrifice of praise shall glorify Me, and there is the way wherein I will show him My salvation.
