Blessed are they that are blameless in the way, who walk in
the law of the Lord.

Blessed are they that search out His testimonies; they shall
seek Him with their whole heart.

For they that work iniquity have not walked in His ways.

Thou hast commanded that Thy commandments be kept most
diligently.

O that my ways may be directed to keep Thy statutes!

Then shall I not be ashamed, when I have respect unto all Thy
commandments.

I will praise Thee with uprightness of heart, when I shall have
learned the judgments of Thy righteousness.

I will keep Thy statutes; O forsake me not utterly.

Wherewithal shall a young man correct his way? even by
keeping Thy words.

With my whole heart have I sought Thee; cast me not away
from Thy commandments.

Thy words have I hid in mine heart, that I might not sin
against Thee.

Blessed art Thou, O Lord; teach me Thy statutes.

With my lips have I declared all the judgments of Thy mouth.

I have had delight in the way of Thy testimonies, as much as
in all riches.

I will meditate on Thy commandments, and understand Thy
ways.

I will meditate in Thy statutes; I will not forget Thy words.

Give recompense unto Thy servant; quicken Thou me, and I
shall keep Thy words.

Open Thou my eyes, and I shall behold the wondrous things
out of Thy law.

I am a stranger in the earth; hide not Thy commandments
from me.

My soul hath longed greatly to desire Thy judgments at all
times.

Thou hast rebuked the proud; cursed are they which do err
from Thy commandments.

Remove from me reproach and contempt, for I have sought
Thy testimonies.

Princes also did sit and speak against me, but Thy servant did
meditate in Thy statutes.

For Thy testimonies are my meditation, and Thy statutes are
my counsels.

My soul hath cleaved unto the dust; quicken Thou me
according to Thy word.

I have declared my ways, and Thou heardest me; teach me
Thy statutes.

Make me to understand the way of Thy precepts, and I will
meditate upon Thy wondrous works.

My soul hath slumbered for heaviness; strengthen Thou me in
Thy words.

Remove from me the way of iniquity, and have mercy upon me
with Thy law.

I have chosen the way of truth, and have not forgotten Thy
judgments.

I have stuck unto Thy testimonies; O Lord, put me not to
shame.

I have run the way of Thy commandments, when Thou hast
enlarged my heart.

Set before me for a law, O Lord, the way of Thy statutes; and I
shall seek it always.

Give me understanding, and I shall seek Thy law; yea, I shall
observe it with my whole heart.

Make me to go in the path of Thy commandments, for I have
longed for it.

Incline my heart to Thy testimonies, and not to covetousness.

Turn away mine eyes, that I behold not vanity; quicken Thou
me in Thy way.

Stablish Thy word unto Thy servant, in fear of Thee.

Take away my reproach which I have feared, for Thy
judgments are good.

Behold, I have longed after Thy precepts; quicken me in Thy
righteousness.

Let Thy mercy come also upon me, O Lord, even Thy salvation,
according to Thy word.

So shall I make answer unto them that reproach me, for I have
hoped in Thy words.

And take not the word of truth utterly out of my mouth, for I
have hoped in Thy judgments.

So shall I keep Thy law continually for ever and ever.

And I walked at liberty, for I sought Thy precepts.

I spake of Thy testimonies also before kings, and was not
ashamed.

And I meditated on Thy commandments, which I have loved
exceedingly.

My hands also have I lifted up unto Thy commandments,
which I have loved; and I meditated in Thy statutes.

Remember Thy words unto Thy servant, upon which Thou
hast caused me to hope.

This hath comforted me in my affliction, for Thy word hath
quickened me.

The proud have transgressed exceedingly, yet have I not
declined from Thy law.

I remembered Thy judgments of old, O Lord, and was
comforted.

Despondency hath taken hold upon me, because of the wicked
that forsake Thy law.

Thy statutes have been my songs in the place of my
pilgrimage.

I have remembered Thy name, O Lord, in the night, and have
kept Thy law.

This happened to me, because I sought Thy precepts.

Thou art my portion, O Lord; I have said that I would keep Thy
law.

I entreated Thy face with my whole heart; be merciful unto me
according to Thy word.

I have thought on Thy ways, and turned my feet unto Thy
testimonies.

I made ready, and was not troubled, that I might keep Thy
commandments.

The cords of the wicked have encompassed me, but I have not
forgotten Thy law.

At midnight I rose to give thanks unto Thee, because of the
judgments of Thy righteousness.

I am a companion of all them that fear Thee, and of them that
keep Thy precepts.

The earth, O Lord, is full of Thy mercy; teach me Thy statutes.

Thou hast dealt graciously with Thy servant, O Lord, according
unto Thy word.

Teach me goodness and discipline and knowledge, for I have
believed Thy commandments.

Before I was humbled I went astray; therefore have I kept Thy
word.

Thou art good, O Lord, and in Thy goodness teach me Thy
statutes.

The injustice of the proud is multiplied against me, but I will
seek Thy commandments with my whole heart.

Their heart is curdled like milk, but I have meditated on Thy
law.

It is good for me that Thou hast humbled me, that I might
learn Thy statutes.

The law of Thy mouth is better to me than thousands of gold
and silver.
