Bless the Lord, O my soul. O Lord my God, Thou art become exceeding magnified.

Thou hast put on praise and majesty; who coverest Thyself with light as with a garment.

Who stretchest out the heavens like a curtain; who supporteth His chambers in the waters.

Who appointeth the clouds for His ascent, who walketh upon the wings of the wind.

Who maketh His angels spirits, and His ministers a flaming fire.

Who hath established the earth upon its sure foundation; it shall not be moved for ever and ever.

The deep like a garment is its mantle; the waters shall stand upon the mountains.

At Thy rebuke they shall flee; at the voice of Thy thunder they shall be afraid.

The mountains rise up, and the plains go down, unto the place which Thou hast founded for them.

Thou hast set a bound that they shall not pass over, neither turn again to cover the earth.

He sendeth the springs into the valleys; the waters shall run among the mountains.

They shall give drink to every beast of the field; the wild asses shall wait to quench their thirst.

By them shall the fowls of the air make their habitation; they shall give voice from the midst of the rocks.

He watereth the mountains from His chambers; the earth shall be satisfied with the fruit of Thy works.

He causeth the grass to grow for the cattle, and green herb for the service of men.

That he may bring forth bread out of the earth: and wine maketh glad the heart of man.

To make his face cheerful with oil: and bread strengtheneth man's heart.

The trees of the plain shall be satisfied, the cedars of Libanus which Thou hast planted.

There shall the sparrows make their nests; the house of the heron is chief among them.

The high mountains are a refuge for the harts, and so is the rock for the hares.

He hath made the moon for seasons; the sun knoweth his going down.

Thou appointedst darkness, and there was night, wherein all the beasts of the forest shall go abroad.

Young lions roaring after their prey, and seeking their meat from God.

The sun arose, and they were gathered together, and they shall lay them down in their dens.

But man shall go forth unto his work, and to his labour until the evening.

O Lord, how magnified are Thy works! In wisdom hast Thou made all things; the earth is filled with Thy creation.

So is this great and wide sea also, wherein are things creeping innumerable, creatures small and great.

There go the ships, there this dragon, whom Thou hast made to play therein.

All things look unto Thee, that Thou mayest give them their meat in due season.

When Thou givest it them, they shall gather it; when Thou openest Thine hand, all things shall be filled with good.

When Thou turnest away Thy face, they shall be troubled; Thou shalt take away their breath, and they shall fail, and return to their dust.

Thou shalt send forth Thy Spirit, and they shall be created, and Thou shalt renew the face of the earth.

Let the glory of the Lord endure for ever; the Lord shall rejoice in His works.

He looketh upon the earth, and maketh it tremble; He toucheth the mountains, and they smoke.

I will sing unto the Lord as long as I live, I will sing praise to my God while I have my being.

Let my words be pleasing unto Him; and I will be glad in the Lord.

O that sinners might be consumed out of the earth, and the workers of iniquity, so that they be no more. Bless thou the Lord, O
my soul.
