I cried unto the Lord with my voice, even unto God with my voice; and He gave ear unto me.

In the day of my trouble I sought God, with my hands lifted up by night before him; and I was not deceived. My soul refused to be comforted.

I remembered God, and I was gladdened; I spake in idleness, and my spirit fainted.

Mine eyes prevented the morning watches; I was troubled, and spake not.

I have considered the days of old, and called to remembrance the years of ages past, and meditated.

I pondered in my heart in the night, and my spirit made diligent search.

Will the Lord cast off for ever? And will He be favourable no more?

Or will He cut off His mercy for ever, his word from generation to generation?

Or will God forget to show mercy? Or will He in his anger shut up His tender mercy for ever?

And I said, Now I have begun; this change is of the right hand of the Most High.

I remembered the works of the Lord, for I will remember Thy wonders of old.

I will meditate also on all Thy works, and consider Thy ways.

Thy way, O God, is in the sanctuary; who is so great a God as our God? Thou art the God that doest wonders.

Thou hast made known Thy strength among the people; Thou hast with Thine arm redeemed Thy people, the sons of Jacob and Joseph.

The waters saw Thee, O God, the waters saw Thee, and were afraid; the depths were troubled.

Great was the noise of the waters; the clouds gave voice, for Thine arrows went abroad.

The voice of Thy thunder was in their rolling, and Thy lightnings lightened the world; the earth trembled and shook.

Thy ways are in the sea, and Thy paths in the great waters; and Thy footsteps shall not be known.

Thou leddest Thy people like sheep, by the hand of Moses and Aaron.
