O give thanks unto the Lord, for He is good; for His mercy endureth for ever.

Who can utter the mighty acts of the Lord? Who can make all His praises to be heard?

Blessed are they that keep judgment, and do righteousness at all times.

Remember us, O Lord, with Thy favour that Thou bearest unto Thy people; O visit us with Thy salvation.

That we may see the good of Thy chosen, that we may rejoice in the gladness of Thy nation, that we may glory with Thine inheritance.

We have sinned with our fathers, we have committed iniquity, we have done wickedly.

Our fathers understood not Thy wonders in Egypt, and they remembered not the multitude of Thy mercy; but provoked Thee as they went up by the Red Sea.

Nevertheless He saved them for His Name's sake, that he might make His mighty power to be known.

He rebuked the Red Sea also, and it was dried up; so He led them into the depths, as in a wilderness.

And He saved them from the hand of him that hated them, and redeemed them from the hand of the enemy.

The waters covered their oppressors; there was not one of them left.

Then believed they His words, and sang His praise.

They made haste, they forgot His works, they waited not for His counsel;

But lusted exceedingly in the wilderness, and tempted God in the desert.

And He gave them their request, and sent fulness into theirsouls.

They provoked Moses also in the camp, and Aaron, the holy one of the Lord.

The earth opened and swallowed up Dathan, and covered the company of Abiron.

And a fire was kindled in their company; the flame burned up the wicked.

And they made a calf in Horeb, and worshipped the graven thing.

Thus they changed His glory into the similitude of a calf that eateth grass.

And they forgot God which had saved them, which had done great things in Egypt,

Wondrous works in the land of Cham, terrible things at the Red Sea.

And He said that He would destroy them, had not Moses His chosen stood before Him in the breach, to turn away His wrath, lest He should destroy them.

Yea, they despised the desirable land; they believed not His
word.

But murmured in their tents; they hearkened not unto the voice of the Lord.

Therefore He lifted up His hand against them, to overthrow them in the wilderness, to overthrow their seed among the nations, and to scatter them in the lands.

They were made initiate also of Baal-phegor, and ate the sacrifices of the dead.

And they provoked Him to anger with their inventions, and destruction was multiplied among them.

And Phineas stood up and made propitiation, and the plague abated. And that was counted unto him for righteousness, from generation to generation for ever.

They provoked Him also at the waters of strife, and Moses was hurt for their sakes.

Because they provoked his spirit, and he gave commandment with his lips.

They did not destroy the nations, concerning whom the Lord commanded them.

They were mingled among the heathen, and learned their works; and they served their graven images, and it became a scandal to them.

Yea, they sacrificed their sons and their daughters unto devils, and shed innocent blood, even the blood of their sons and of their daughters, whom they sacrificed to the graven things of Canaan.

And the land was murderously defiled with blood, and was polluted with their own works, and they went aside after their own inventions.

Therefore was the wrath of the Lord kindled against His people, and He abhorred His own inheritance.

And He gave them into the hand of the enemy, and they that hated them were lords over them.

Their enemies also afflicted them, and they were brought down into subjection under their hand.

Many times did He deliver them, but they provoked him with their counsel, and were brought low in their iniquities

Nevertheless the Lord regarded them in their afflition, and heard their supplication.

And He remembered His covenant, and repented according to the multitude of His mercy.

He made them to be pitied in the sight of all those that had taken them captive.

Save us, O Lord our God, and gather us from among the heathen, that we may give thanks unto Thy holy Name, that we may glory in Thy praise.

Blessed be the God of Israel, from everlasting to everlasting; and all the peoples shall say: So be it, so be it.
