In Thee, O Lord, have I put my hope, let me never be ashamed. Deliver me in Thy righteousness, and rescue me; incline Thine ear unto me, and save me.

Be Thou unto me a defending God, and a strong habitation to save me, for Thou art my rock and my refuge.

Deliver me, O my God, out of the hand of the sinner, out of the hand of the transgressor and unrighteous man.

For Thou art mine endurance, O Lord; O Lord, Thou art my hope from my youth.

On Thee have I been holden up from the womb; from my mother's belly Thou art my protector. My song of praise is continually of Thee.

I am as a wonder unto many, but Thou art my strong helper.

Let my mouth be filled with Thy praise, that I may hymn Thy glory, Thy majesty all the day.

Cast me not off in the time of old age; forsake me not when my strength faileth.

For mine enemies spake against me, and they that lay wait for my soul took counsel together,

Saying: God hath forsaken him; persecute and take him, for there is none to deliver him.

My God, be not far from me; O my God, make haste for my help.

Let them be ashamed and brought to nought that slander my soul; let them be covered with shame and confusion that seek my hurt.

But I will hope in Thee continually, and will yet praise Thee more and more.

My mouth shall show forth Thy righteousness, Thy salvation all the day; for I know not the reckoning thereof.

I will go in the strength of the Lord; O Lord, I will make mention of Thy righteousness, which is Thine only.

My God, Thou hast taught me from my youth, and until now will I declare Thy wondrous works.

Until I am old and greyheaded, my God, forsake me not; until I have showed Thy mighty arm to every generation that is to come;

Thy power and Thy righteousness, O God, and show even to the highest the great things which Thou hast done for me. O God, who is like unto Thee?

How great are the troubles which Thou hast shown me, many and evil; yet Thou hast turned and quickened me, and hast brought me up again from the depths of the earth.

Thou hast multiplied Thy magnificence over me, and returning, Thou hast comforted me, and hast brought me up again from the depths of the earth.

Therefore I will praise Thee among the people, O Lord, with instruments of psalmody; unto Thee with the harp will I sing of Thy truth, O God, the Holy One of Israel.

My lips shall greatly rejoice when I sing unto Thee, and my soul, which Thou hast redeemed.

My tongue also shall meditate on Thy righteousness all the day long, when they are brought unto shame, and confounded, that seek my hurt.
