Rejoice in the Lord, O ye righteous; praise becometh the upright.

Praise the Lord with the harp; sing unto Him with the psaltery of ten strings.

Sing unto Him a new song; sing skilfully unto Him with jubilation.

For the word of the Lord is right, and all His works are done in faithfulness.

The Lord loveth mercy and judgment; the earth is full of the mercy of the Lord.

By the word of the Lord were the heavens made, and all the host of them by the breath of His mouth.

He gathereth the waters of the sea together, as in a wineskin; He layeth up the depths in storehouses.

Let all the earth fear the Lord, and let all the inhabitants of the world be moved in awe of Him.

For He spake, and they were made; He commanded, and they were created.

The Lord bringeth the counsels of the heathen to nought, He setteth aside the devices of the people, and maketh the counsels of the princes to be of none effect.

But the counsel of the Lord standeth for ever, the thoughts of His heart to all generations.

Blessed is the nation whose God is the Lord, and the people whom He hath chosen for His own inheritance.

The Lord looked from heaven; He beheld all the sons of men.

From the place of His habitation that He prepared, He looked upon all the inhabitants of the earth.

He that alone fashioneth their heart, that considereth all their works.

There is no king saved by much power, nor shall a mighty man be delivered by the multitude of his strength.

A horse is a vain thing for safety, neither shall he be saved by his great strength.

Behold, the eyes of the Lord are upon them that fear Him, upon them that hope in His mercy.

To deliver their souls from death, and to nourish them in famine.

Our soul shall wait for the Lord, for He is our help and our defence.

For our heart shall rejoice in Him, and we have hoped in His holy Name.

Let Thy mercy, O Lord, be upon us, according as we have hoped in Thee.
