I waited patiently for the Lord, and He inclined unto me, and heard my supplication.

He brought me up also out of the pit of misery, and out of the miry clay, and set my feet upon a rock, and established my goings.

And He hath put a new song in my mouth, even praise unto our God. Many shall see it, and fear, and shall hope in the Lord.

Blessed is the man whose hope is in the Name of the Lord, and regardeth not vanities and false frenzies.

Many, O Lord my God, are Thy wonderful works which Thou hast done; and in Thy Thoughts there is none that shall be compared to Thee. I declared and spake, They are multiplied beyond number.

Sacrifice and offering Thou didst not desire, but a body hast Thou perfected for me; burnt offering and sin offering hast Thou not required.

Then said I, Lo, I come. In the head of the book it is written of me,

That I should do Thy will, O my God; yea, Thy law is within my heart.

I have preached the good tidings of Thy righteousness in the great congregation. Lo, I shall not refrain my lips, O Lord, Thou knowest.

I have not hid Thy righteousness within my heart; I have declared Thy faithfulness and Thy salvation. I have not concealed Thy mercy and Thy truth from the great congregation.

But withhold not Thou Thy tender mercies from me, O Lord; let Thy mercy and Thy truth continually help me.

For innumerable evils have compassed me about; mine iniquities have taken hold upon me, and I am not able to see. They are multiplied more than the hairs of mine head, and my heart hath failed me.

Be pleased, O Lord, to deliver me; O Lord, make haste to help me.

Let them be ashamed and confounded together that seek after my soul to destroy it. Let them be driven backward and confounded that wish me evil.

Let them quickly receive shame for their reward that say unto me, Well well!

Let all those that seek Thee rejoice and be glad in Thee, O Lord; and let such as love Thy salvation say continually, The Lord be magnified.

But I am poor and needy; the Lord will take thought for me. Thou art my help and my defender, my God; make no tarrying.
