We have heard with our ears, O God, for our fathers have told us the work Thou didst in their days, in the days of old.

Thy hand hand destroyed the heathen, and in their stead Thou dids't plant them; Thou didst bring evils upon those people, and cast them out.

For not by their own sword did they inherit the land, neither did their own arm save them:

But it was Thy right hand, and Thine arm, and the light of Thy countenance, because Thou wast well pleased with them.

Thou Thyself art my King and my God, Thou that commandest the salvation of Jacob.

Through Thee will the horn of our strength push down our enemies, and through Thy Name will we bring to nought them that rise up against us.

For I will not hope in my bow, neither shall my sword save me.

For Thou hast saved us from them that troubled us, and hast put them to shame that hated us.

In God will we boast all the day long, and in Thy Name will we give thanks for ever.

But now Thou hast cast us off, and put us to shame, and Thou, O God wilt not go forth with our hosts.

Thou hast made us to turn back before our enemies, and they which hated us took spoils for themselves.

Thou hast given us up like sheep to be eaten, and hast scattered us among the heathen.

Thou hast sold Thy people for nought, and there was no profit by our selling.

Thou hast made us a reproach to our neighbours, a scorn and derision to them that are round about us.

Thou hast made us a byword among the heathen, a shaking of the head among the peoples.

All the day long my humiliation is before me, and the shame of my face hath covered me,

Because of the voice of him that slandereth and revileth, because of the face of the enemy and pursuer.

All this is come upon us, yet we have not forgotten Thee, neither have we dealt unrighteously in Thy covenant.

Though our heart is not turned back, yet Thou hast turned aside our paths from Thy ways.

For Thou hast humbled us in a place of affliction, and the shadow of death hath covered us.

If we have forgotten the Name of our God, and if we have stretched out our hands to a strange god,

Shall not God search this out? For He knoweth the secrets of the heart.

For Thy sake are we slain all the day long; we are counted as sheep for the slaughter.

Awake, why sleepest Thou, O Lord? Arise, and cast us not off for ever.

Wherefore hidest Thou Thy face? Dost Thou forget our poverty and affliction?

For our soul is brought down to the dust; our belly hath cleaved unto the earth.

Arise, O Lord, help us, and redeem us for Thy Name's sake.
