Hear my prayer, O Lord, and let my cry come unto Thee.

Turn not away Thy face from me; in the day when I am in trouble incline Thine ear unto me; in the day when I call unto Thee, make haste to hear me.

For my days have vanished like smoke, and my bones are consumed like wood for burning.

I am smitten like grass, and my heart is withered, for I forgot to eat my bread.

By reason of the voice of my groaning, my bone hath cleaved to my flesh.

I am become like a pelican of the wilderness; I am become like an owl within a ruined house.

I have watched, and am become as a sparrow that sitteth alone upon the housetop.

Mine enemies reproached me all the day, and they that praised me are sworn against me.

For I have eaten ashes like bread, and mingled my drink with weeping, because of Thine indignation and Thy wrath:

For Thou hast lifted me up, and cast me down.

My days have declined like a shadow, and I am withered like grass.

But Thou, O Lord, endurest for ever, and Thy remembrance from generation to generation.

Thou shalt arise, and have mercy upon Sion; for it is time to have mercy upon on her, yea, the time is come.

For Thy servants have taken pleasure in her stones, and they shall have pity for the dust thereof.

And the heathen shall fear Thy Name, O Lord, and all the kings of the earth Thy glory.

For the Lord shall build up Sion, and He shall be seen in His glory.

He hath regarded the prayer of the humble, and hath not despised their supplication.

Let this be written for a generation to come, and the people which shall be created shall praise the Lord.

For He hath looked out from His holy height; out of heaven did the Lord behold the earth,

To hear the groaning of the prisoners; to deliver the sons of the slain;

To declare the Name of the Lord in Sion, and His praise in Jerusalem.

When the people are gathered together, and the kings, to serve the Lord.

He answered him in the way of his strength, Declare unto me the fewness of my days.

Take me not away in the midst of my days; Thy years are from generation to generation.

Thou, Lord, in the beginning didst lay the foundations of the earth, and the heavens are the work of Thy hands.

They shall perish, but Thou endurest; yea, they shall all wax old as a garment, and as a vesture shalt Thou fold them, and they
shall be changed.

But Thou art the same, and Thy years shall not fail.

The sons of Thy servants shall dwell, and their seed shall be guided aright for ever.
