Bless the Lord, O my soul, and all that is within me bless His holy name.

Bless the Lord, O my soul, and forget not all His benefits.

Who forgiveth all thine iniquities, who healeth all thine infirmities.

Who redeemeth thy life from corruption, who crowneth thee with mercy and compassion.

Who satisfieth thy desire with good things; thy youth shall be renewed like the eagle's.

The Lord executeth mercy and judgment for all them that are wronged.

He made known His ways unto Moses, His will unto the children of Israel.

The Lord is compassionate and merciful, long-suffering and plenteous in mercy. He will not always be angry, neither will He be wrathful for ever.

He hath not dealt with us after our sins, nor rewarded us according to our iniquities.

For as the heaven is high above the earth, the Lord hath made His mercy to prevail over them that fear Him.

As far as the east is from the west, so far hath He removed our iniquities from us.

Like as a father hath compassion upon his children, so hath the Lord compassion on them that fear Him; for He knoweth whereof we are made, He remembereth that we are dust.

As for man, his days are as the grass; as a flower of the field, so shall he flourish.

For when the wind hath passed over it, it shall be gone, and it will know the place thereof no more.

But the mercy of the Lord is from everlasting to everlasting upon them that fear Him.

And His righteousness upon children's children, upon such as keep His testament, and remember His commandments to do them.

The Lord hath prepared His throne in heaven, and His kingdom ruleth over all.

Bless the Lord, all ye His angels, mighty in strength, that perform His word, to hearken unto the voice of His words.

Bless ye the Lord, all ye His hosts, ye ministers of His that do His pleasure.

Bless the Lord, all ye works of His, in all places of His dominion. Bless the Lord, O my soul.
