Save me, O God, for the waters are come in unto my soul. I am stuck fast in the deep mire, and there is no standing. I am come into the depths of the sea, and a tempest hath overwhelmed me.

I am weary with my crying, my throat is become hoarse; mine eyes have failed from hoping in my God.

They that hate me without a cause are multiplied more than the hairs of my head; mine enemies are grown strong that persecute me wrongfully; then I restored that which I took not away.

O God, Thou knowest my foolishness, and my sins are not hid from Thee.

Let not those that wait on Thee, O Lord, Thou Lord of hosts, be ashamed for my sake; nor let them that seek Thee be confounded for my sake, O God of Israel.

Because for Thy sake I have borne reproach; shame hath covered my face.

I am become a stranger unto my brethren, and an alien unto my mother's children.

For the zeal of Thine house hath eaten me up, and the reproaches of them that reproach Thee are fallen upon me.

And I covered my soul with fasting, and that was made a reproach unto me.

I made sackcloth also my garment, and I became a proverb unto them.

They that sit in the gate spake against me, and the drunkards made me their song.

But as for me, with my prayer will I cry unto Thee, O Lord, for the time of Thy good pleasure. O God, in the multitude of Thy mercy hear me, in the truth of Thy salvation.

Deliver me out of the mire, that I may not stick fast; let me be delivered from them that hate me, and out of the deep waters.

Let not the waterflood overflow me, neither let the deep swallow me up, and let not the pit shut her mouth upon me.

Hear me, O Lord, for Thy mercy is good; according to the multitude of Thy tender mercies look upon me.

Turn not away Thy face from Thy servant, for I am in trouble; hear me speedily.

Draw nigh unto my soul, and redeem it; deliver me because of mine enemies.

For Thou knowest my reproach, and my shame, and my humiliation. All they that afflict me are before Thee.

My soul hath looked for reproach and misery; and I looked for one that would grieve with me, but there was none; and for one that would comfort me, but found I none.

They gave me also gall for my meat, and for my thirst they gave me vinegar to drink.

Let their table become a snare before them, for a recompense, and for a stumbling block.

Let their eyes be darkened, that they see not, and bow down their back continually.

Pour out Thine indignation upon them, and let Thy wrathful anger take hold upon them.

Let their habitation be desolate, and let none dwell in their tents.

For they persecuted him whom Thou hast smitten, and have added to the pain of my wounds.

Add iniquity unto their iniquity, and let them not come into Thy righteousness.

Let them be blotted out of the book of the living, and not be written with the righteous.

I am poor and sorrowful; let Thy salvation, O God, be quick to help me.

I will praise the Name of my God with a song; I will magnify Him with thanksgiving.

This also shall please God better than a young calf that hath horns and hoofs.

Let the needy see this, and be glad; seek ye God, and your soul shall live.

For the Lord hath heard the poor, and hath not despised His prisoners.

Let the heaven and earth praise Him; the sea and every thing that creepeth therein.

For God will save Sion, and the cities of Judea shall be built up; and they shall dwell there, and inherit it.

The seed also of Thy servants shall have it in possession, and they that love Thy Name shall dwell therein.
